### 2018-04-02 proposal/main.tex
Proposal .tex file

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Fatness of Simple Polygons}
\author{Sharmila Duppala \and David Kraemer}
\date{April 2018}

\begin{document}

\maketitle

\section{Problem Statement}

Computing the Niceness of a Polygonal Shape. There are various notions of
quantifying how “nice” or how “fat” a simple polygon $P$ is. A “nicest” polygon
might be a regular n-gon, which most closely approximates a circular disk. This
project seeks to implement some precise metrics for niceness, and compare them
on simple polygons (possibly moused in by a user or read in from a file, etc).
To make it simple and discrete, I propose that you discretize the boundary of
$P$
with discrete points pi (additional vertices), with a prescribed spacing,
$\delta$. (That is, for edges of $P$ longer than $\delta$, add vertices along the
edge so that the new sub-segments are of length at most $\delta$, for a
user-specified parameter $\delta$.)

Then, consider discrete choices of radii $r = \rho, 2\rho, 3\rho, \ldots$ for
disks, $B(p_i,r)$, centered at the discrete boundary points $p_i$, for each
radius $r$. The (discrete) fatness of $P$ is given by the smallest value of the
ratio $area(B(p_i,r)\cap P)/area(B(p_i, r)$, over all choices of $p_i$ and $r =
  \rho, 2\rho, 3\rho$, . . . such that $P$ is not contained fully
  inside$B(p_i,r)$.

Implement and experiment with this fatness measure. It may be possible to use
the algorithm to assist a project at Harvard on Gerrymandering, where the goal
is to quantify how “compact” polygonal election districts are. (So I hope that
at least a couple of people choose to do this project! We can discuss further.)

(Theoretically, we are interested in finding an algorithm to compute the “exact”
fatness of $P$ (which allows disks centered anywhere inside $P$, of any radius
such that the disk does not contain all of $P$), without resorting to the simple
discretization. Or, can we compute a provable approximation to the exact
fatness?)

\section{Inferences and Questions}
The decomposition of the polygon results in some fat Polygons as well as some bad Polygons. We see that a fat Polygon is made a bad Polygon by inserting the bad polygon. This makes me wonder about the union of the Simple Polygons NICE+BAD, BAD+BAD, NICE+NICE. 
\subsubsection{Questions} 
\begin{enumerate}
\item Q1: Given a Simple Polygon, does it fatness depend on the fatness of the
  individual polygons its made of?
\item Q2: So, for an individual polygon, without loss of generality lets assume that every Simple Polygon is made up of triangles. So, to measure the fatness of a polygon, we  have to measure the fatness of a triangle. So, the next question we ask ourselves is the fatness of any given triangle, the simplest polygon.
\item
Q3: Can we get the fatness of the triangle using the $\alpha$-fatness using the formula given above, whereas is it possible to use squares instead of circles as we know our boundary is a Polygon with straight lines but not a curve.
Q4: About the defnition of the $\alpha-fatness$
Q5: Why do we have to discretize the 
Q6: Alternative measures like, possibly bad unions of nice polygons or visibility kernal ratio. 
Q7: 
\end{enumerate}

\section{Implementation}

\end{document}

### 2018-04-02 proposal/main.tex
Proposal

@@
 \documentclass{article}
+
 \usepackage[utf8]{inputenc}
+\usepackage[]{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+
+\newcommand{\RR}{\mathbb{R}}
+\newcommand{\abs}[1]{\vert#1\vert}
+\DeclareMathOperator*{\argmin}{\textrm{arg\,min}}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
 
@@
 
+[From Professor Mitchell's description.]
 Computing the Niceness of a Polygonal Shape. There are various notions of
 quantifying how “nice” or how “fat” a simple polygon $P$ is. A “nicest” polygon
-might be a regular n-gon, which most closely approximates a circular disk. This
+might be a regular $n$-gon, which most closely approximates a circular disk. This
 project seeks to implement some precise metrics for niceness, and compare them
@@
 To make it simple and discrete, I propose that you discretize the boundary of
-$P$
-with discrete points pi (additional vertices), with a prescribed spacing,
-$\delta$. (That is, for edges of $P$ longer than $\delta$, add vertices along the
-edge so that the new sub-segments are of length at most $\delta$, for a
+$P$ with discrete points $p_i$ (additional vertices), with a prescribed spacing,
+$\delta$. (That is, for edges of $P$ longer than $\delta$, add vertices along
+  the edge so that the new sub-segments are of length at most $\delta$, for a
 user-specified parameter $\delta$.)
@@
 radius $r$. The (discrete) fatness of $P$ is given by the smallest value of the
-ratio $area(B(p_i,r)\cap P)/area(B(p_i, r)$, over all choices of $p_i$ and $r =
-  \rho, 2\rho, 3\rho$, . . . such that $P$ is not contained fully
+ratio $\lambda (B(p_i,r)\cap P)/\lambda (B(p_i, r)$, over all choices of $p_i$ and $r =
+  \rho, 2\rho, 3\rho, \ldots$ such that $P$ is not contained fully
   inside$B(p_i,r)$.
@@
 
-\section{Inferences and Questions}
-The decomposition of the polygon results in some fat Polygons as well as some bad Polygons.
+\section{Definitions}
+
+Our present objective is to develop rigorous measures of the ``niceness'' of
+simple bounded closed planar polygons with the intuitive hierarchy that regular
+$n$-gons are ``nicest'' followed by convex $n$-gons and proceeded by ``fat''
+polygons---i.e., polygons which retain their structure under smoothing filters.
+
+Throughout we assume that $P \subseteq \RR^2$ is a simple bounded closed
+polygon. We shall denote by $\partial P$ the boundary of $P$, with
+$\abs{\partial P}$ denoting the perimeter and $\lambda(P)$ denoting the area.
+For given points $x,y \in \RR$, denote the closed line segment bounded by $x$
+and $y$ by $[x,y]$.  The class of such polygons is denoted by $\mathcal{P}$.
+
+One class of ``fatness'' measures arises through partitioning $P$ into two
+(interior disjoint) polygons $P = P' \cup P''$ via chords.  A chord is a pair
+$x,y \in \partial P$ such that the segment $[x,y]$ is contained by the relative
+interior of $P$ except at the endpoints $x$ and $y$.  Such a chord $[x,y]$
+defines a partition of $P = P' \cup P''$ by orientation, so that $\partial P'$
+is the arc from $x$ to $y$ with $[y,x]$ and that $\partial P''$ is the arc from
+$y$ to $x$ with $[x,y]$.
+
+\begin{definition}
+  Let $f : \mathcal{P} \to \RR$. For a given $P \in \mathcal{P}$,
+  its \emph{chord-$f$ score} is given by
+  \begin{equation*}
+    s_f(P) = \min_{x,y \in P} \max(f(P'), f(P''))
+  \end{equation*}
+  where the chord $[x,y]$ partitions $P = P' \cup P''$.
+\end{definition}
+
+Intuitively, $f$ represents a polygon's cost with respect to a certain
+measurement.  For example, if $f$ indicates the perimeter of $P$, then $s_f$ is
+associated with a partition of $P$ such that the maximum perimeter of either
+subpolygon is minimized. Indeed, measures such as perimeter or area are the
+typical choices of $f$, but any suitable property of the polygon may be
+employed.
+
+The visibility kernel of $P$, denoted by $\ker P$, is the subset of $P$ which
+``sees'' all of $P$. That is, if $x \in \ker P$ and $y \in P$, then $[x,y]
+\subseteq P$. Another proposed measure of polygonal ``niceness'' utilizes the
+visibility kernel.
+
+\begin{definition}
+  The \emph{visibility kernel score} is given by
+  \begin{equation*}
+    s_{\textrm{vis}}(P) = \frac{\lambda(\ker P)}{\lambda(P)}.
+  \end{equation*}
+\end{definition}
+
+If $P$ is a regular $n$-gon or convex $s_{\textrm{vis}}(P) = 1$, since trivially
+$\ker P = P$. On the other hand, if $P$ is not star shaped, then
+$s_{\textrm{vis}}(P) = 0$.
+
+%\section{Inferences and Questions}
+%The decomposition of the polygon results in some fat Polygons as well as some bad Polygons.
 We see that a fat Polygon is made a bad Polygon by inserting the bad polygon.
 This makes me wonder about the union of the Simple Polygons NICE+BAD, BAD+BAD, NICE+NICE.
-\subsubsection{Questions} 
-\begin{enumerate}
-\item Q1: Given a Simple Polygon, does it fatness depend on the fatness of the
-  individual polygons its made of?
-\item Q2: So, for an individual polygon, without loss of generality lets assume that every Simple Polygon is made up of triangles.
+%\subsubsection{Questions} 
+%\begin{enumerate}
+%\item Q1: Given a Simple Polygon, does it fatness depend on the fatness of the
+%  individual polygons its made of?
+%\item Q2: So, for an individual polygon, without loss of generality lets assume that every Simple Polygon is made up of triangles.
 So, to measure the fatness of a polygon, we  have to measure the fatness of a triangle.
 So, the next question we ask ourselves is the fatness of any given triangle, the simplest polygon.
-\item
-Q3: Can we get the fatness of the triangle using the $\alpha$-fatness using the formula given above, whereas is it possible to use squares instead of circles as we know our boundary is a Polygon with straight lines but not a curve.
-Q4: About the defnition of the $\alpha-fatness$
-Q5: Why do we have to discretize the 
-Q6: Alternative measures like, possibly bad unions of nice polygons or visibility kernal ratio. 
-Q7: 
-\end{enumerate}
+%\item
+%Q3: Can we get the fatness of the triangle using the $\alpha$-fatness using the formula given above, whereas is it possible to use squares instead of circles as we know our boundary is a Polygon with straight lines but not a curve.
+%Q4: About the defnition of the $\alpha-fatness$
+%Q5: Why do we have to discretize the 
+%Q6: Alternative measures like, possibly bad unions of nice polygons or visibility kernal ratio. 
+%Q7: 
+%\end{enumerate}
 
@@
 
+We plan to implement these measures of polygonal ``fatness'' and compare them
+for assorted collections of polygons, from theoretical and
+randomly-generated examples to historical electoral map data. We hope to
+determine the relative strengths of these measures as heuristics for polygonal
+``fatness'' individually or in an ensemble on this data.
+
 \end{document}

### 2018-04-04 proposal/main.tex
Finished proposal

@@
-\documentclass{article}
+\documentclass[10pt]{article}
 
 \usepackage[utf8]{inputenc}
+\usepackage[margin=1in]{geometry}
 \usepackage[]{amsmath}
@@
 \newcommand{\abs}[1]{\vert#1\vert}
+\newcommand{\set}[1]{\{#1\}}
 \DeclareMathOperator*{\argmin}{\textrm{arg\,min}}
@@
 
-[From Professor Mitchell's description.]
+\paragraph{Professor Mitchell's description.}
 Computing the Niceness of a Polygonal Shape. There are various notions of
@@
 radius $r$. The (discrete) fatness of $P$ is given by the smallest value of the
-ratio $\lambda (B(p_i,r)\cap P)/\lambda (B(p_i, r)$, over all choices of $p_i$ and $r =
-  \rho, 2\rho, 3\rho, \ldots$ such that $P$ is not contained fully
-  inside$B(p_i,r)$.
+ratio $\lambda (B(p_i,r)\cap P)/\lambda (B(p_i, r))$, over all choices of $p_i$
+and $r = \rho, 2\rho, 3\rho, \ldots$ such that $P$ is not contained fully inside
+$B(p_i,r)$.
 
@@
   is to quantify how “compact” polygonal election districts are. (So I hope that
-at least a couple of people choose to do this project! We can discuss further.)
+  at least a couple of people choose to do this project! We can discuss
+further.)
 
@@
   fatness of $P$ (which allows disks centered anywhere inside $P$, of any radius
-such that the disk does not contain all of $P$), without resorting to the simple
-discretization. Or, can we compute a provable approximation to the exact
-fatness?)
+  such that the disk does not contain all of $P$), without resorting to the
+  simple discretization. Or, can we compute a provable approximation to the
+exact fatness?)
 
@@
   \begin{equation*}
-    s_f(P) = \min_{x,y \in P} \max(f(P'), f(P''))
+    s_f(P) = \inf_{x,y \in \partial P} \max(f(P'), f(P''))
   \end{equation*}
@@
 
-%\section{Inferences and Questions}
-%The decomposition of the polygon results in some fat Polygons as well as some bad Polygons.
-We see that a fat Polygon is made a bad Polygon by inserting the bad polygon.
-This makes me wonder about the union of the Simple Polygons NICE+BAD, BAD+BAD, NICE+NICE.
-%\subsubsection{Questions} 
-%\begin{enumerate}
-%\item Q1: Given a Simple Polygon, does it fatness depend on the fatness of the
-%  individual polygons its made of?
-%\item Q2: So, for an individual polygon, without loss of generality lets assume that every Simple Polygon is made up of triangles.
-So, to measure the fatness of a polygon, we  have to measure the fatness of a triangle.
-So, the next question we ask ourselves is the fatness of any given triangle, the simplest polygon.
-%\item
-%Q3: Can we get the fatness of the triangle using the $\alpha$-fatness using the formula given above, whereas is it possible to use squares instead of circles as we know our boundary is a Polygon with straight lines but not a curve.
-%Q4: About the defnition of the $\alpha-fatness$
-%Q5: Why do we have to discretize the 
-%Q6: Alternative measures like, possibly bad unions of nice polygons or visibility kernal ratio. 
-%Q7: 
-%\end{enumerate}
+Equipped with an $L_p$ norm ($p \in [1,\infty]$), denote by $B(x,\rho)$ the
+closed ball of radius $\rho > 0$ centered at $x \in \RR^2$.  The natural choice
+is simply the Euclidean norm, but $L_{\infty}$ provides a setting for which
+computing $B(x,\rho) \cap P$ resolves to polygonal intersection. By topological
+equivalence, we lose no specificity. A final measure of ``fatness'' measures
+local nonconvexities of $P$ and identifies the most offending ratio.
+\begin{definition}
+  The \emph{$\alpha$-fatness score} is given by
+  \begin{equation*}
+    \alpha(P) = \inf\set{\frac{\lambda(B(x,\rho) \cap
+    P)}{\lambda(B(x,\rho))} : x \in \partial P, \rho > 0, P \not\subseteq B(x,\rho)}
+  \end{equation*}
+\end{definition}
+
+For a given $S \subseteq \RR^2$, let $\mathcal{C}(x,S)$ denote the connected
+component of $S$ containing $x$. An alternative formulation of $\alpha$-fatness
+replaces $B(x,\rho) \cap P$ with its connected component: $\mathcal{C}(x,
+B(x,\rho) \cap P)$. In principle, $\alpha(P)$ is computed by sweeping
+continuously, but for simplicity we can merely discretize $\partial P$ with a
+parameter $\delta > 0$ indicating the maximal distance between points in
+$\partial P$.
 

### 2018-04-05 polygonal-niceness/polygon2d.cpp
Attempted to implement delta refinement.

@@ -1,0 +1,51 @@
+#include "polygon2d.h"
+#include <CGAL/squared_distance_2.h>
+#include <iostream>
+
+void Polygon2D::refine(double delta_sqr) {
+  auto origin = _pol.vertices_begin();
+  auto current = origin;
+  auto next = current;
+  ++next;
+  auto traversing = true;
+  auto index = 1; // index of next insertion
+
+  do {
+    auto dist_sqr = CGAL::squared_distance(*current, *next);
+    if (delta_sqr < dist_sqr) { // insert a midpoint
+      auto & midpoint = Point_2(
+          ((*current).x() + (*next).x() ) / 2,
+          ((*current).y() + (*next).y() ) / 2);
+      std::cout << midpoint << std::endl;
+      _pol.insert(index, midpoint);
+      next = current;
+      ++next;
+    }
+    else {
+      traversing = (*next == *origin);
+
+      index++;
+      ++current;
+    }
+
+  } while (traversing);
+}
+
+bool Polygon2D::is_refined(double delta_sqr) {
+  auto origin = _pol.vertices_begin();
+  auto current = origin;
+  auto next = current;
+
+  auto traversing = true;
+
+  do {
+    ++next;
+    traversing = (*next == *origin);
+    auto dist_sqr = CGAL::squared_distance(*current, *next);
+    if (delta_sqr < dist_sqr) {
+      return false;
+    }
+  } while (traversing);
+
+  return true;
+}

### 2018-04-05 polygonal-niceness/polygon2d.h

@@ -1,0 +1,33 @@
+#ifndef POLYGON_2D_H
+#define POLYGON_2D_H
+#include <CGAL/Simple_cartesian.h>
+#include <CGAL/Polygon_2.h>
+//#include <CGAL/Intersection_2.h>
+#include <cmath>
+
+template<typename T>
+constexpr T pi = T(3.14159265358979323846264338);
+
+typedef CGAL::Simple_cartesian<double> K;
+typedef K::Point_2 Point_2;
+typedef K::Segment_2 Segment_2;
+typedef CGAL::Polygon_2<K> Polygon_2;
+typedef K::Intersect_2 Intersect_2;
+
+class Polygon2D {
+  public:
+    Polygon2D(Polygon_2 p) : _pol(p) {}
+
+    void refine(double delta_sqr);
+    bool is_refined(double delta_sqr);
+    double area() { return _pol.area(); }
+    bool is_convex() { return _pol.is_convex(); }
+    bool is_simple() { return _pol.is_simple(); }
+
+    Point_2 operator[](int index) { return _pol[index]; }
+    
+  private:
+    Polygon_2 _pol;
+};
+
+#endif

### 2018-04-05 polygonal-niceness/main.cpp
Updated main.

@@ -1,18 +1,24 @@
-#include <iostream>
-#include <CGAL/Simple_cartesian.h>
-
-typedef CGAL::Simple_cartesian<double> Kernel;
-typedef Kernel::Point_2 Point2D;
-typedef Kernel::Segment_2 Segment2D;
+#include "polygon2d.h"
 
 int main() {
-  Point2D p(1,1), q(10,10);
+  for (int n = 8; n < 9; n++) {
+    Point_2 points[n];
+    for (int i = 0; i < n; i++)
+      points[i] = Point_2(std::cos(i * 2*pi<double> / n), std::sin(i * 2*pi<double> / n));
 
-  std::cout << "p = " << p << std::endl;
-  std::cout << "q = " << q.x() << " " << q.y() << std::endl;
+    Polygon2D pol(Polygon_2(points, points+n));
 
-  std::cout << "sqdist(p,q) = " 
-    << CGAL::squared_distance(p,q) << std::endl;
+    auto delta = 0.5;
+
+    std::cout << pol[0] << std::endl;
+
+    std::cout << "Area: " << pol.area() << std::endl;
+    std::cout << "Convex?: " << pol.is_convex() << std::endl;
+    std::cout << "Simple?: " << pol.is_simple() << std::endl;
+    std::cout << delta << "-refined?: " << pol.is_refined(delta*delta) << std::endl;
+    // pol.refine(delta*delta);
+
+  }
 
   return 0;
 

### 2018-04-05 playgrouond/polygon2d.cpp
Updates, attempted a new version of refinement... still not working.

@@ -1,0 +1,18 @@
+#include <CGAL/Simple_cartesian.h>
+#include <CGAL/Polygon_2.h>
+#include <cmath>
+
+template<typename T>
+constexpr T pi = T(3.14159265358979323846264338);
+
+typedef CGAL::Simple_cartesian<double> K;
+typedef K::Point_2 Point_2;
+typedef K::Segment_2 Segment_2;
+typedef CGAL::Polygon_2<K> Polygon_2;
+
+
+int main() {
+  int n = 5;
+
+  return 0;
+}

### 2018-04-05 polygonal-niceness/main.cpp

@@ -1,24 +1,27 @@
 #include "polygon2d.h"
 
 int main() {
-  for (int n = 8; n < 9; n++) {
-    Point_2 points[n];
-    for (int i = 0; i < n; i++)
-      points[i] = Point_2(std::cos(i * 2*pi<double> / n), std::sin(i * 2*pi<double> / n));
+  int n = 3;
+  Point_2 points[n];
+  for (int i = 0; i < n; i++)
+    points[i] = Point_2(std::cos(i * 2*pi<double> / n), std::sin(i * 2*pi<double> / n));
 
-    Polygon2D pol(Polygon_2(points, points+n));
+  Polygon2D p(Polygon_2(points, points+n));
 
-    auto delta = 0.5;
+  auto delta = 0.5;
 
-    std::cout << pol[0] << std::endl;
+  for (int i = 0; i < p.size(); i++)
+    std::cout << p[i] << std::endl;
 
-    std::cout << "Area: " << pol.area() << std::endl;
-    std::cout << "Convex?: " << pol.is_convex() << std::endl;
-    std::cout << "Simple?: " << pol.is_simple() << std::endl;
-    std::cout << delta << "-refined?: " << pol.is_refined(delta*delta) << std::endl;
-    // pol.refine(delta*delta);
+  std::cout << std::endl;
 
-  }
+
+
+  Polygon2D q= refine(p, delta);
+  for (auto v : p)
+    std::cout << v << std::endl;
+
+
 
   return 0;
 

### 2018-04-05 polygonal-niceness/polygon2d.cpp

@@ -1,34 +1,49 @@
 #include "polygon2d.h"
 #include <CGAL/squared_distance_2.h>
 #include <iostream>
+#include <vector>
 
-void Polygon2D::refine(double delta_sqr) {
-  auto origin = _pol.vertices_begin();
-  auto current = origin;
-  auto next = current;
-  ++next;
-  auto traversing = true;
-  auto index = 1; // index of next insertion
+Polygon2D refine(Polygon2D p, double delta) {
+  auto points = std::vector<Point_2>(p.size());
+  auto refined_size = p.size();
 
-  do {
-    auto dist_sqr = CGAL::squared_distance(*current, *next);
-    if (delta_sqr < dist_sqr) { // insert a midpoint
-      auto & midpoint = Point_2(
-          ((*current).x() + (*next).x() ) / 2,
-          ((*current).y() + (*next).y() ) / 2);
-      std::cout << midpoint << std::endl;
-      _pol.insert(index, midpoint);
-      next = current;
-      ++next;
-    }
-    else {
-      traversing = (*next == *origin);
+  for (int i = 0; i < p.size(); i++) { // for each existing point in p,
+    // add the point to the new polygon
+    
+    points.push_back(Point_2(p[i].x(), p[i].y()));
 
-      index++;
-      ++current;
-    }
+    // if (i+1 < p.size()) { // if the next point exists,
+    //   // compute the distance between the points
+    //   
+    //   auto current = points.back();
+    //   auto dist_sqr = CGAL::squared_distance(p[i+1],current);
+    //   auto dist = std::sqrt(dist_sqr); // unfortunate, don't know how to fix
 
-  } while (traversing);
+    //   if (delta*delta < dist_sqr) { // if the distance is too big,
+    //     // add new points according to an equidistance scheme
+
+    //     int insertions = std::ceil(dist / delta) - 1; // number of new points needed
+
+    //     // parameterize the line segment 
+    //     double x0 = current.x();
+    //     double y0 = current.y();
+    //     double dx = p[i+1].x() - x0;
+    //     double dy = p[i+1].y() - y0;
+    //     
+    //     // normalize
+    //     dx /= insertions + 1;
+    //     dy /= insertions + 1;
+
+    //     for (int j = 0; j < insertions; j++) {
+    //       // insert a new point
+    //       points.push_back(Point_2(x0 + (j+1) * dx, y0 + (j+1) * dy));
+    //     }
[…]

### 2018-04-05 polygonal-niceness/polygon2d.h

@@ -18,16 +18,20 @@ class Polygon2D {
   public:
     Polygon2D(Polygon_2 p) : _pol(p) {}
 
-    void refine(double delta_sqr);
-    bool is_refined(double delta_sqr);
+    bool is_refined(double delta);
     double area() { return _pol.area(); }
     bool is_convex() { return _pol.is_convex(); }
     bool is_simple() { return _pol.is_simple(); }
+    int size() { return _pol.size(); }
+    int* begin() { return _pol.begin(); }
+    int* end() { return _pol.end(); }
 
     Point_2 operator[](int index) { return _pol[index]; }
     
   private:
     Polygon_2 _pol;
 };
+
+Polygon2D refine(Polygon2D p, double delta_sqr);
 
 #endif

### 2018-04-25 polygonal-niceness/io_utils.cpp
Alpha fatness implemented but breaking

@@ -1,9 +1,11 @@
 #include "io_utils.h"
-  std::vector<std::vector<double>> generate_data(
-      std::function<Polygon2D(int)> poly_generator,
-      std::tuple<const int, const int, const int> n_range,
-      std::tuple<const double, const double, const int> delta_linspace,
-      std::function<double(Polygon2D)> measurement)
+
+
+std::vector<std::vector<double>> generate_data(
+    std::function<Polygon2D(int)> poly_generator, 
+    std::tuple<const int, const int, const int> n_range,
+    std::tuple<const double, const double, const int> delta_linspace,
+    std::function<double(Polygon2D)> measurement)
 {
 
   std::vector<std::vector<double>> data(0);
@@ -35,6 +37,7 @@
 
   return data;
 }
+
 
 void write_data(
     std::vector<std::vector<double>> data, 

### 2018-04-25 polygonal-niceness/main.cpp

@@ -5,18 +5,21 @@
 int main() {
   std::function<Polygon2D(int)> generator = nth_roots_of_unity;
 
-  auto data = generate_data(
-      generator,
-      std::make_tuple(3,103,1),
-      std::make_tuple(1e-4,1e-3,3),
-      chord_area_measurement);
+  auto p = generator(4);
+  std::cout << alpha_fatness(p) << std::endl;
 
-  std::vector<std::string> header {"n","1e-4","5e-4","1e-3"};
+  // auto data = generate_data(
+  //     generator,
+  //     std::make_tuple(3,103,1),
+  //     std::make_tuple(1e-4,1e-3,3),
+  //     alpha_fatness);
 
-  write_data (
-      data,
-      header,
-      "data/regular_ngon_chord_area_scores.csv");
+  // std::vector<std::string> header {"n","1e-4","5e-4","1e-3"};
+
+  // write_data (
+  //     data,
+  //     header,
+  //     "data/regular_ngon_alpha_fatness_scores.csv");
 
   return 0;
 }

### 2018-04-25 polygonal-niceness/measurements.h

@@ -1,9 +1,11 @@
 #ifndef _MEASUREMENTS_H
 #define _MEASUREMENTS_H
 
-double farea(Polygon2D p) {
+std::function<double(Polygon2D)> farea = [](Polygon2D p) {
   return p.area();
-}
+};
+
+std::function<double(Polygon2D)> alpha_fatness = alpha_fatness_score;
 
 double regular_ngon_area_normalizer(int n) {
   return n / 2 * std::sin(2 * pi<double> / n);
@@ -17,8 +19,8 @@ Polygon2D nth_roots_of_unity(int n) {
   return Polygon2D(Polygon_2(points, points+n));
 }
 
-std::function<double(Polygon2D)> chord_area_measurement = [](Polygon2D p) { 
-    return p.area() / regular_ngon_area_normalizer(p.size()); 
-};
+//std::function<double(Polygon2D)> chord_area_measurement = [](Polygon2D p) { 
+//    return p.area();
+//};
 
 #endif

### 2018-04-25 polygonal-niceness/polygon2d.cpp

@@ -78,6 +78,7 @@ bool Polygon2D::is_refined_by(double delta)
   return true;
 }
 
+
 double chord_f_score(Polygon2D &p, std::function<double(Polygon2D)> f)
 {
   double min = f(p);
@@ -134,6 +135,62 @@ double chord_f_score(Polygon2D &p, std::function<double(Polygon2D)> f)
 
   return min;
 }
+
+
+double alpha_fatness_score(Polygon2D p)
+{
+  auto min_alpha = std::numeric_limits<double>::infinity();
+  auto bbox_coords = p.bbox_coords();
+
+  for (auto& vertex: p)
+  {
+    auto max_radius = std::max(
+        std::max(vertex.x() - std::get<0>(bbox_coords),
+          std::get<2>(bbox_coords) - vertex.x()),
+        std::max(vertex.y() - std::get<1>(bbox_coords),
+          std::get<3>(bbox_coords) - vertex.y())
+        );
+
+    for (auto k = 50; k < 100; k+= 49) 
+    {
+      auto radius = k * max_radius / 100.;
+      Polygon2D ball = infinity_ball(vertex, radius);
+      auto area = intersection_area(p, ball);
+      min_alpha = std::min(min_alpha, area / (4 * radius * radius));
+    }
+    
+  }
+
+  return min_alpha;
+}
+
+
+Polygon2D infinity_ball(Point_2 &v, double radius)
+{
+  std::vector<Point_2> corners(4);
+
+  corners.push_back(Point_2(v.x() - radius, v.y() - radius));
+  corners.push_back(Point_2(v.x() + radius, v.y() - radius));
+  corners.push_back(Point_2(v.x() + radius, v.y() + radius));
+  corners.push_back(Point_2(v.x() - radius, v.y() + radius));
+  return Polygon2D(Polygon_2(corners.data(), corners.data() + corners.size()));
+}
+
+double intersection_area(Polygon2D &p, Polygon2D &q)
+{
+  std::list<Polygon_with_holes_2> result;
+  CGAL::intersection(p._pol, q._pol, std::back_inserter(result));
+
+  double area = 0.;
+  for (auto iter = result.begin(); iter != result.end(); iter++)
+  {
+    area += iter->outer_boundary().area();
+  }
+
+
+  return area;
+}
+
 
 /* 
  * The following is lifted almost entirely from O'Rourke's text, "Computational

### 2018-04-25 polygonal-niceness/polygon2d.h

@@ -1,8 +1,14 @@
 #ifndef _POLYGON_2D_H
 #define _POLYGON_2D_H
+
 #include <CGAL/Simple_cartesian.h>
 #include <CGAL/Polygon_2.h>
+#include <CGAL/Polygon_with_holes_2.h>
+#include <CGAL/Boolean_set_operations_2.h>
+#include <CGAL/Polygon_2_algorithms.h>
+
 #include <cmath>
+#include <limits>
 
 template<typename T>
 constexpr T pi = T(3.14159265358979323846264338);
@@ -11,6 +17,7 @@ typedef CGAL::Simple_cartesian<double> K;
 typedef K::Point_2 Point_2;
 typedef K::Segment_2 Segment_2;
 typedef CGAL::Polygon_2<K> Polygon_2;
+typedef CGAL::Polygon_with_holes_2<K> Polygon_with_holes_2;
 typedef K::Intersect_2 Intersect_2;
 
 class Segment2D {
@@ -34,17 +41,33 @@ class Polygon2D {
     int size() { return _pol.size(); }
     auto begin() { return _pol.vertices_begin(); }
     auto end() { return _pol.vertices_end(); }
+    std::tuple<double,double,double,double> bbox_coords() {
+      return std::make_tuple(
+          _pol.left_vertex()->x(),
+          _pol.bottom_vertex()->y(),
+          _pol.right_vertex()->x(),
+          _pol.top_vertex()->y()
+          );
+    }
 
     Point_2 operator[](int index) { return _pol[index]; }
     
-  private:
     Polygon_2 _pol;
 };
 
-bool is_chord(Segment2D seg, Polygon2D p);
 
 Polygon2D refinement_by(Polygon2D &p, double delta_sqr);
+Polygon2D infinity_ball(Point_2 &v, double radius);
+
 double chord_f_score(Polygon2D &p, std::function<double(Polygon2D)> f);
+double alpha_fatness_score(Polygon2D p);
+
+double intersection_area(Polygon2D &p, Polygon2D &q);
+
+
+/* Utility functions */
+
+bool is_chord(Segment2D seg, Polygon2D p);
 double area2(Point_2 p, Point_2 q, Point_2 r);
 bool is_left(Segment2D seg, Point_2 p);
 bool is_collinear(Segment2D seg, Point_2 p);

### 2018-04-27 polygonal-niceness/io_utils.cpp
Major reorganization and updates
The code now compiles with exact arithmetic. The files have been reorganized in a saner fashion. Not sure if the programs themselves work yet, that's the next test.

@@ -1,18 +1,18 @@
 #include "io_utils.h"
 
 
-std::vector<std::vector<double>> generate_data(
+std::vector<std::vector<K::FT>> generate_data(
     std::function<Polygon2D(int)> poly_generator, 
     std::tuple<const int, const int, const int> n_range,
-    std::tuple<const double, const double, const int> delta_linspace,
-    std::function<double(Polygon2D)> measurement)
+    std::tuple<const K::FT, const K::FT, const int> delta_linspace,
+    std::function<K::FT(Polygon2D)> measurement)
 {
 
-  std::vector<std::vector<double>> data(0);
+  std::vector<std::vector<K::FT>> data(0);
   for (int n = std::get<0>(n_range); n < std::get<1>(n_range); 
       n += std::get<2>(n_range))
   {
-    std::vector<double> ndata(0);
+    std::vector<K::FT> ndata(0);
 
     // label the nth row
     ndata.push_back(n);
@@ -26,7 +26,7 @@ std::vector<std::vector<double>> generate_data(
         std::get<2>(delta_linspace);
 
       // refine p for the next delta
-      Polygon2D q = refinement_by(p, delta);
+      Polygon2D q = refinement_by(p, (K::FT) delta);
 
       // compute the corresponding measurement and store the result
       ndata.push_back(measurement(q));
@@ -40,7 +40,7 @@ std::vector<std::vector<double>> generate_data(
 
 
 void write_data(
-    std::vector<std::vector<double>> data, 
+    std::vector<std::vector<K::FT>> data, 
     std::vector<std::string> header,
     std::string output_file)
 {

### 2018-04-27 polygonal-niceness/io_utils.h

@@ -1,19 +1,25 @@
 #ifndef _IO_UTILS_H
 #define _IO_UTILS_H
-#include "polygon2d.h"
+
+
+#include <tuple>
 #include <vector>
 #include <string>
-#include <tuple>
 #include <fstream>
 
-std::vector<std::vector<double>> generate_data(
+
+#include "kernel_specs.h"
+#include "polygon2d.h"
+
+
+std::vector<std::vector<K::FT>> generate_data(
     std::function<Polygon2D(int)> poly_generator,
     std::tuple<const int, const int, const int> n_range,
-    std::tuple<const double, const double, const int> delta_linspace,
-    std::function<double(Polygon2D)> measurement);
+    std::tuple<const K::FT, const K::FT, const int> delta_linspace,
+    std::function<K::FT(Polygon2D)> measurement);
 
 void write_data(
-    std::vector<std::vector<double>> data, 
+    std::vector<std::vector<K::FT>> data, 
     std::vector<std::string> header,
     std::string output_file);
 

### 2018-04-27 polygonal-niceness/kernel_specs.h

@@ -1,0 +1,18 @@
+#ifndef _KERNEL_SPECS_H
+#define _KERNEL_SPECS_H
+
+
+#include <CGAL/Exact_predicates_exact_constructions_kernel.h>
+#include <CGAL/Polygon_2.h>
+#include <CGAL/Polygon_with_holes_2.h>
+#include <CGAL/Boolean_set_operations_2.h>
+
+
+typedef CGAL::Exact_predicates_exact_constructions_kernel K;
+typedef K::Point_2 Point_2;
+typedef K::Segment_2 Segment_2;
+typedef CGAL::Polygon_2<K> Polygon_2;
+typedef CGAL::Polygon_with_holes_2<K> Polygon_with_holes_2;
+
+
+#endif 

### 2018-04-27 polygonal-niceness/main.cpp

@@ -1,12 +1,15 @@
+#include "kernel_specs.h"
 #include "polygon2d.h"
+#include "niceness_functions.h"
 #include "io_utils.h"
 #include "measurements.h"
 
-int main() {
-  std::function<Polygon2D(int)> generator = nth_roots_of_unity;
 
-  auto p = generator(4);
-  std::cout << alpha_fatness(p) << std::endl;
+int main()
+{
+  std::cout << "Hello world!" << std::endl;
+  // auto p = square_of_length(12);
+  // std::cout << chord_f_score(p, chord_area_measurement) << std::endl;
 
   // auto data = generate_data(
   //     generator,

### 2018-04-27 polygonal-niceness/measurements.h

@@ -1,26 +1,25 @@
 #ifndef _MEASUREMENTS_H
 #define _MEASUREMENTS_H
 
-std::function<double(Polygon2D)> farea = [](Polygon2D p) {
+
+#include "kernel_specs.h"
+#include "polygon2d.h"
+
+
+std::function<K::FT(Polygon2D)> farea = [](Polygon2D p) {
   return p.area();
 };
 
-std::function<double(Polygon2D)> alpha_fatness = alpha_fatness_score;
+std::function<K::FT(Polygon2D)> alpha_fatness = alpha_fatness_score;
 
-double regular_ngon_area_normalizer(int n) {
-  return n / 2 * std::sin(2 * pi<double> / n);
+Polygon2D square_of_length(int n) 
+{
+  Point_2 points[4];
+  points[0] = Point_2(0,0);
+  points[1] = Point_2(n,0);
+  points[2] = Point_2(n,n);
+  points[2] = Point_2(0,n);
+  return Polygon2D(Polygon_2(points, points+4));
 }
-
-Polygon2D nth_roots_of_unity(int n) {
-  Point_2 points[n];
-  for (int i = 0; i < n; i++)
-    points[i] = Point_2(std::cos(i * 2*pi<double> / n), std::sin(i * 2*pi<double> / n));
-
-  return Polygon2D(Polygon_2(points, points+n));
-}
-
-//std::function<double(Polygon2D)> chord_area_measurement = [](Polygon2D p) { 
-//    return p.area();
-//};
 
 #endif

### 2018-04-27 polygonal-niceness/niceness_functions.cpp

@@ -1,0 +1,119 @@
+#include "niceness_functions.h"
+#include "predicates.h"
+
+
+K::FT chord_f_score(Polygon2D &p, std::function<K::FT(Polygon2D)> f)
+{
+  K::FT min = std::numeric_limits<K::FT>::infinity();
+
+  // Loop through all possible pairs of vertices in p
+  for (int i = 0; i < p.size(); i++)
+  {
+    for (int j = i+1; j < p.size(); j++)
+    {
+      // Test that the segment [p[i],p[j]] is a chord of p
+      if (is_chord(Segment2D(p[i],p[j]), p)) 
+      {
+        // NOTE: this is almost certainly an inefficient way of doing this, but
+        // whatever.
+        auto left_points = std::vector<Point_2>(j - i + 1);
+        auto right_points = std::vector<Point_2>(p.size() - j + 1 + i);
+
+        // insert the points which are between p[i] and p[j] to the "left" 
+        for (auto k = i; k <= j; k++) 
+        { 
+          left_points.push_back(p[k]);
+        }
+
+        // insert the points which are between p[i] and p[j] to the "right"
+        for (auto k = j; k < p.size(); k++) 
+        { // this half of the insertion is until the end of the polygon
+          right_points.push_back(p[k]);
+        }
+
+        for (auto k = 0; k <= i; k++)
+        { // this half of the insertion is from the beginning of the polygon until i
+          right_points.push_back(p[k]);
+        }
+
+        // compute the sub-polygons
+        Polygon2D left_sub(
+            Polygon_2(
+              left_points.data(),
+              left_points.data() + left_points.size()
+            ));
+
+        Polygon2D right_sub(
+            Polygon_2(
+              right_points.data(),
+              right_points.data() + right_points.size()
+              ));
+        
+        // update the minimum f-score
+        min = CGAL::min(min, CGAL::max(f(left_sub), f(right_sub)));
+      }
+    }
+  }
+
+
+  return min;
+}
+
+
+K::FT alpha_fatness_score(Polygon2D p)
+{
+  auto min_alpha = std::numeric_limits<K::FT>::infinity();
+  auto bbox_coords = p.bbox_coords();
+
+  for (auto& vertex: p)
+  {
+    auto max_radius = std::max(
+        std::max(vertex.x() - std::get<0>(bbox_coords),
[…]

### 2018-04-27 polygonal-niceness/niceness_functions.h

@@ -1,0 +1,16 @@
+#ifndef _NICENESS_FUNCTIONS_H
+#define _NICENESS_FUNCTIONS_H
+
+
+#include "kernel_specs.h"
+#include "polygon2d.h"
+
+
+
+Polygon2D infinity_ball(Point_2 &v, K::FT radius);
+
+K::FT chord_f_score(Polygon2D &p, std::function<K::FT(Polygon2D)> f);
+K::FT alpha_fatness_score(Polygon2D p);
+K::FT intersection_area(Polygon2D &p, Polygon2D &q);
+
+#endif

### 2018-04-27 polygonal-niceness/polygon2d.cpp

@@ -1,64 +1,20 @@
 #include "polygon2d.h"
+
+
 #include <CGAL/squared_distance_2.h>
-#include <iostream>
+#include <CGAL/Boolean_set_operations_2.h>
+
+
 #include <vector>
-
-#define XOR(lb,rb) (!(lb) ^ !(rb))
-
-Polygon2D refinement_by(Polygon2D &p, double delta)
-{
-  auto points = std::vector<Point_2>(p.size());
-  auto next = p[0];
-
-  for (int i = 0; i < p.size(); i++) 
-  { // for each existing point in p,
-
-    // add the point to the new polygon
-    points.push_back(Point_2(p[i].x(), p[i].y()));
-
-    // is there another point? if so, that's next; otherwise, next is the start.
-    next = p[(i + 1) % p.size()];
-
-    // compute the distance between the points
-    auto current = points.back();
-    auto dist_sqr = CGAL::squared_distance(next, current);
-    auto dist = std::sqrt(dist_sqr); // actual distance is needed, unfortunately
-
-    if (delta*delta < dist_sqr) 
-    { // if the distance is too big,
-      // add new points according to an equidistance scheme
-
-      auto insertions = std::ceil(dist / delta); // number of new points needed
-
-      // parameterize the line segment 
-      auto x0 = current.x();
-      auto y0 = current.y();
-      auto dx = next.x() - x0;
-      auto dy = next.y() - y0;
-
-      // normalize
-      dx /= insertions;
-      dy /= insertions;
+#include <stack>
+#include <limits>
 
 
-      for (int j = 1; j < insertions; j++)
-      {
-        // insert a new point
-        points.push_back(Point_2(x0 + j * dx, y0 + j * dy));
-      }
-    }
-  }
+void _compute_edge_refinement(Point_2 source, Point_2 target, K::FT delta, std::vector<Point_2> &points);
 
-  points.shrink_to_fit();
-  return Polygon2D(
-      Polygon_2(
-        points.data(),
-        points.data() + points.size()
-        )
-      );
-}
 
-bool Polygon2D::is_refined_by(double delta)
+
+bool Polygon2D::is_refined_by(K::FT delta)
 {
   auto delta_sqr = delta * delta;
   auto origin = _pol[0];
@@ -78,193 +34,53 @@ bool Polygon2D::is_refined_by(double delta)
   return true;
 }
 
-
[…]

### 2018-04-27 polygonal-niceness/polygon2d.h

@@ -1,24 +1,9 @@
 #ifndef _POLYGON_2D_H
 #define _POLYGON_2D_H
 
-#include <CGAL/Simple_cartesian.h>
-#include <CGAL/Polygon_2.h>
-#include <CGAL/Polygon_with_holes_2.h>
-#include <CGAL/Boolean_set_operations_2.h>
-#include <CGAL/Polygon_2_algorithms.h>
 
-#include <cmath>
-#include <limits>
+#include "kernel_specs.h"
 
-template<typename T>
-constexpr T pi = T(3.14159265358979323846264338);
-
-typedef CGAL::Simple_cartesian<double> K;
-typedef K::Point_2 Point_2;
-typedef K::Segment_2 Segment_2;
-typedef CGAL::Polygon_2<K> Polygon_2;
-typedef CGAL::Polygon_with_holes_2<K> Polygon_with_holes_2;
-typedef K::Intersect_2 Intersect_2;
 
 class Segment2D {
   public:
@@ -34,14 +19,14 @@ class Polygon2D {
   public:
     Polygon2D(Polygon_2 p) : _pol(p) {}
 
-    bool is_refined_by(double delta);
-    double area() { return _pol.area(); }
+    bool is_refined_by(K::FT delta);
+    K::FT area() { return _pol.area(); }
     bool is_convex() { return _pol.is_convex(); }
     bool is_simple() { return _pol.is_simple(); }
     int size() { return _pol.size(); }
     auto begin() { return _pol.vertices_begin(); }
     auto end() { return _pol.vertices_end(); }
-    std::tuple<double,double,double,double> bbox_coords() {
+    std::tuple<K::FT,K::FT,K::FT,K::FT> bbox_coords() {
       return std::make_tuple(
           _pol.left_vertex()->x(),
           _pol.bottom_vertex()->y(),
@@ -55,25 +40,7 @@ class Polygon2D {
     Polygon_2 _pol;
 };
 
+Polygon2D refinement_by(Polygon2D &p, K::FT delta);
 
-Polygon2D refinement_by(Polygon2D &p, double delta_sqr);
-Polygon2D infinity_ball(Point_2 &v, double radius);
-
-double chord_f_score(Polygon2D &p, std::function<double(Polygon2D)> f);
-double alpha_fatness_score(Polygon2D p);
-
-double intersection_area(Polygon2D &p, Polygon2D &q);
-
-
-/* Utility functions */
-
[…]

### 2018-04-27 polygonal-niceness/predicates.cpp

@@ -1,0 +1,79 @@
+#include "predicates.h"
+
+
+/* 
+ * The following is lifted almost entirely from O'Rourke's text, "Computational
+ * Geometry in C".
+ */
+
+bool is_chord(Segment2D seg, Polygon2D p) 
+{
+  for (auto i = 0; i < p.size(); i++)
+  {
+    auto j = (i + 1) % p.size();
+    if ((p[i] != seg.source()) && (p[j] != seg.source())
+      && (p[i] != seg.target()) && (p[j] != seg.target())
+        && intersect(seg, Segment2D(p[i], p[j])))
+        {
+          return false;
+        }
+  }
+  return true;
+}
+
+bool intersect(Segment2D s1, Segment2D s2) 
+{
+  return intersect_properly(s1, s2) ||
+    is_between(s1, s2.source()) ||
+    is_between(s1, s2.target()) ||
+    is_between(s2, s1.source()) ||
+    is_between(s2, s1.target());
+}
+
+bool is_between(Segment2D seg, Point_2 p) 
+{
+  if (!is_collinear(seg, p)) 
+  {
+    return false;
+  }
+
+  if (seg.source().x() != seg.target().x())
+  {
+    return ((seg.source().x() <= p.x()) && (p.x() <= seg.target().x())) || 
+      ((seg.source().x() >= p.x()) && (p.x() >= seg.target().x()));
+  } 
+  else
+  {
+    return ((seg.source().y() <= p.y()) && (p.y() <= seg.target().y())) || 
+      ((seg.source().y() >= p.y()) && (p.y() >= seg.target().y()));
+  }
+}
+
+bool intersect_properly(Segment2D s1, Segment2D s2)
+{
+  if (is_collinear(s1, s2.source()) ||
+      is_collinear(s1, s2.target()) ||
+      is_collinear(s2, s1.source()) ||
+      is_collinear(s2, s1.target()))
+  {
+    return false;
+  }
+
+  return XOR(is_left(s1, s2.source()), is_left(s1, s2.target())) &&
+    XOR(is_left(s2, s1.source()), is_left(s2, s1.target()));
+}
+
+bool is_collinear(Segment2D seg, Point_2 p)
+{
+  return area(seg.source(), seg.target(), p) == 0.;
+}
+
+bool is_left(Segment2D seg, Point_2 p)
+{
+  return area(seg.source(), seg.target(), p) > 0.;
+}
+
[…]

### 2018-04-27 polygonal-niceness/predicates.h

@@ -1,0 +1,23 @@
+#ifndef _PREDICATES_H
+#define _PREDICATES_H
+
+
+#include "kernel_specs.h"
+#include "polygon2d.h"
+
+
+#define XOR(lb,rb) (!(lb) ^ !(rb))
+
+
+/* Predicate functions */
+
+bool is_chord(Segment2D seg, Polygon2D p);
+K::FT area(Point_2 p, Point_2 q, Point_2 r);
+bool is_left(Segment2D seg, Point_2 p);
+bool is_collinear(Segment2D seg, Point_2 p);
+bool intersect_properly(Segment2D s1, Segment2D s2);
+bool is_between(Segment2D seg, Point_2 p);
+bool intersect(Segment2D s1, Segment2D s2);
+bool is_chord(Segment2D seg, Polygon2D p);
+
+#endif

### 2018-04-27 polygonal-niceness/main.cpp
Everything works!
Hooray!!!

@@ -7,9 +7,10 @@
 
 int main()
 {
-  std::cout << "Hello world!" << std::endl;
-  // auto p = square_of_length(12);
-  // std::cout << chord_f_score(p, chord_area_measurement) << std::endl;
+  auto p = square_of_length(12);
+  std::cout << p << std::endl;
+  auto q = refinement_by(p, 4);
+  std::cout << q << std::endl;
 
   // auto data = generate_data(
   //     generator,

### 2018-04-27 polygonal-niceness/measurements.h

@@ -18,7 +18,7 @@ Polygon2D square_of_length(int n)
   points[0] = Point_2(0,0);
   points[1] = Point_2(n,0);
   points[2] = Point_2(n,n);
-  points[2] = Point_2(0,n);
+  points[3] = Point_2(0,n);
   return Polygon2D(Polygon_2(points, points+4));
 }
 

### 2018-04-27 polygonal-niceness/niceness_functions.cpp

@@ -4,36 +4,36 @@
 
 K::FT chord_f_score(Polygon2D &p, std::function<K::FT(Polygon2D)> f)
 {
-  K::FT min = std::numeric_limits<K::FT>::infinity();
+  K::FT min = f(p);
 
   // Loop through all possible pairs of vertices in p
   for (int i = 0; i < p.size(); i++)
   {
-    for (int j = i+1; j < p.size(); j++)
+    for (int j = i+2; j < p.size(); j++)
     {
       // Test that the segment [p[i],p[j]] is a chord of p
-      if (is_chord(Segment2D(p[i],p[j]), p)) 
+      if (is_chord(i, j, p)) 
       {
         // NOTE: this is almost certainly an inefficient way of doing this, but
         // whatever.
-        auto left_points = std::vector<Point_2>(j - i + 1);
-        auto right_points = std::vector<Point_2>(p.size() - j + 1 + i);
+        std::vector<Point_2> left_points;
+        std::vector<Point_2> right_points;
 
         // insert the points which are between p[i] and p[j] to the "left" 
         for (auto k = i; k <= j; k++) 
         { 
-          left_points.push_back(p[k]);
+          left_points.push_back(Point_2(p[k].x(), p[k].y()));
         }
 
         // insert the points which are between p[i] and p[j] to the "right"
         for (auto k = j; k < p.size(); k++) 
         { // this half of the insertion is until the end of the polygon
-          right_points.push_back(p[k]);
+          right_points.push_back(Point_2(p[k].x(), p[k].y()));
         }
 
         for (auto k = 0; k <= i; k++)
         { // this half of the insertion is from the beginning of the polygon until i
-          right_points.push_back(p[k]);
+          right_points.push_back(Point_2(p[k].x(), p[k].y()));
         }
 
         // compute the sub-polygons
@@ -55,32 +55,29 @@ K::FT chord_f_score(Polygon2D &p, std::function<K::FT(Polygon2D)> f)
     }
   }
 
-
   return min;
 }
 
 
 K::FT alpha_fatness_score(Polygon2D p)
 {
-  auto min_alpha = std::numeric_limits<K::FT>::infinity();
+  K::FT min_alpha = 100;
   auto bbox_coords = p.bbox_coords();
 
   for (auto& vertex: p)
   {
-    auto max_radius = std::max(
[…]

### 2018-04-27 polygonal-niceness/niceness_functions.h

@@ -6,7 +6,6 @@
 #include "polygon2d.h"
 
 
-
 Polygon2D infinity_ball(Point_2 &v, K::FT radius);
 
 K::FT chord_f_score(Polygon2D &p, std::function<K::FT(Polygon2D)> f);

### 2018-04-27 polygonal-niceness/polygon2d.cpp

@@ -34,9 +34,10 @@ bool Polygon2D::is_refined_by(K::FT delta)
   return true;
 }
 
+
 Polygon2D refinement_by(Polygon2D &p, K::FT delta)
 {
-  auto points = std::vector<Point_2>(p.size());
+  auto points = std::vector<Point_2>();
   auto next = p[0];
 
   for (int i = 0; i < p.size(); i++) 
@@ -58,7 +59,6 @@ Polygon2D refinement_by(Polygon2D &p, K::FT delta)
 void _compute_edge_refinement(Point_2 source, Point_2 target, 
     K::FT delta, std::vector<Point_2> &points)
 {
-  points.push_back(Point_2(source.x(), source.y()));
   auto curr = source;
   auto next = target;
   auto temp = next;
@@ -80,7 +80,36 @@ void _compute_edge_refinement(Point_2 source, Point_2 target,
     }
   }
 
-  points.push_back(Point_2(target.x(), target.y()));
-
 }
+
+
+
+std::ostream& operator<<(std::ostream &os, const Point_2 &p)
+{
+  os << "(" << p.x() << "," << p.y() << ")";
+  return os;
+}
+
+std::ostream& operator<<(std::ostream &os, const Segment2D &seg)
+{
+  os << "[" << seg.source() << "," << seg.target() << "]";
+  return os;
+}
+
+std::ostream& operator<<(std::ostream &os, const Polygon2D &pol)
+{
+  os << "<";
+  for (int i = 0; i < pol.size(); i++)
+  {
+    os << pol[i];
+    if (i + 1 < pol.size())
+    {
+      os << ",";
+    }
+  }
+  os << ">";
+
+  return os;
+}
+
 

### 2018-04-27 polygonal-niceness/polygon2d.h

@@ -5,13 +5,15 @@
 #include "kernel_specs.h"
 
 
+#include <ostream>
+
+
 class Segment2D {
   public:
     Segment2D(Point_2 p1, Point_2 p2) : _seg(p1, p2) {}
     Point_2 source() const { return _seg.source(); }
     Point_2 target() const { return _seg.target(); }
     
-  private:
     Segment_2 _seg;
 };
 
@@ -23,7 +25,7 @@ class Polygon2D {
     K::FT area() { return _pol.area(); }
     bool is_convex() { return _pol.is_convex(); }
     bool is_simple() { return _pol.is_simple(); }
-    int size() { return _pol.size(); }
+    int size() const { return _pol.size(); }
     auto begin() { return _pol.vertices_begin(); }
     auto end() { return _pol.vertices_end(); }
     std::tuple<K::FT,K::FT,K::FT,K::FT> bbox_coords() {
@@ -35,12 +37,16 @@ class Polygon2D {
           );
     }
 
-    Point_2 operator[](int index) { return _pol[index]; }
+    Point_2 operator[](int index) const { return _pol[index]; }
     
     Polygon_2 _pol;
 };
 
 Polygon2D refinement_by(Polygon2D &p, K::FT delta);
+
+std::ostream& operator<<(std::ostream &os, const Point_2 &p);
+std::ostream& operator<<(std::ostream &os, const Segment2D &seg);
+std::ostream& operator<<(std::ostream &os, const Polygon2D &pol);
 
 
 #endif

### 2018-04-27 polygonal-niceness/predicates.cpp

@@ -6,74 +6,28 @@
  * Geometry in C".
  */
 
-bool is_chord(Segment2D seg, Polygon2D p) 
+bool is_chord(int i, int j, Polygon2D &p) 
 {
-  for (auto i = 0; i < p.size(); i++)
+  for (auto k = 0; k < p.size(); k++)
   {
-    auto j = (i + 1) % p.size();
-    if ((p[i] != seg.source()) && (p[j] != seg.source())
-      && (p[i] != seg.target()) && (p[j] != seg.target())
-        && intersect(seg, Segment2D(p[i], p[j])))
-        {
-          return false;
-        }
+    auto m = (k + 1) % p.size();
+    if (!(
+          (k == i) || (m == i) ||
+          (k == j) || (m == j)
+         )
+       )
+    {
+      std::cout << "(" << k << "," << m << ")" << std::endl;
+      if (intersect(Segment2D(p[i],p[j]), Segment2D(p[k], p[m])))
+      {
+        return false;
+      }
+    }
   }
   return true;
 }
 
 bool intersect(Segment2D s1, Segment2D s2) 
 {
-  return intersect_properly(s1, s2) ||
-    is_between(s1, s2.source()) ||
-    is_between(s1, s2.target()) ||
-    is_between(s2, s1.source()) ||
-    is_between(s2, s1.target());
-}
-
-bool is_between(Segment2D seg, Point_2 p) 
-{
-  if (!is_collinear(seg, p)) 
-  {
-    return false;
-  }
-
-  if (seg.source().x() != seg.target().x())
-  {
-    return ((seg.source().x() <= p.x()) && (p.x() <= seg.target().x())) || 
-      ((seg.source().x() >= p.x()) && (p.x() >= seg.target().x()));
-  } 
-  else
-  {
-    return ((seg.source().y() <= p.y()) && (p.y() <= seg.target().y())) || 
-      ((seg.source().y() >= p.y()) && (p.y() >= seg.target().y()));
-  }
-}
-
-bool intersect_properly(Segment2D s1, Segment2D s2)
-{
-  if (is_collinear(s1, s2.source()) ||
-      is_collinear(s1, s2.target()) ||
-      is_collinear(s2, s1.source()) ||
-      is_collinear(s2, s1.target()))
-  {
-    return false;
-  }
-
-  return XOR(is_left(s1, s2.source()), is_left(s1, s2.target())) &&
[…]

### 2018-04-27 polygonal-niceness/predicates.h

@@ -11,13 +11,7 @@
 
 /* Predicate functions */
 
-bool is_chord(Segment2D seg, Polygon2D p);
-K::FT area(Point_2 p, Point_2 q, Point_2 r);
-bool is_left(Segment2D seg, Point_2 p);
-bool is_collinear(Segment2D seg, Point_2 p);
-bool intersect_properly(Segment2D s1, Segment2D s2);
-bool is_between(Segment2D seg, Point_2 p);
+bool is_chord(int i, int j, Polygon2D &p);
 bool intersect(Segment2D s1, Segment2D s2);
-bool is_chord(Segment2D seg, Polygon2D p);
 
 #endif

### 2018-04-27 polygonal-niceness/polygon2d.cpp
Minor stuff

@@ -13,7 +13,6 @@
 void _compute_edge_refinement(Point_2 source, Point_2 target, K::FT delta, std::vector<Point_2> &points);
 
 
-
 bool Polygon2D::is_refined_by(K::FT delta)
 {
   auto delta_sqr = delta * delta;
@@ -56,12 +55,13 @@ Polygon2D refinement_by(Polygon2D &p, K::FT delta)
       );
 }
 
+
 void _compute_edge_refinement(Point_2 source, Point_2 target, 
     K::FT delta, std::vector<Point_2> &points)
 {
   auto curr = source;
   auto next = target;
-  auto temp = next;
+
   std::stack<Point_2> next_stack;
   next_stack.push(target);
 
@@ -83,18 +83,19 @@ void _compute_edge_refinement(Point_2 source, Point_2 target,
 }
 
 
-
 std::ostream& operator<<(std::ostream &os, const Point_2 &p)
 {
   os << "(" << p.x() << "," << p.y() << ")";
   return os;
 }
 
+
 std::ostream& operator<<(std::ostream &os, const Segment2D &seg)
 {
   os << "[" << seg.source() << "," << seg.target() << "]";
   return os;
 }
+
 
 std::ostream& operator<<(std::ostream &os, const Polygon2D &pol)
 {
@@ -111,5 +112,3 @@ std::ostream& operator<<(std::ostream &os, const Polygon2D &pol)
 
   return os;
 }
-
-

### 2018-04-27 polygonal-niceness/polygon2d.h

@@ -17,6 +17,7 @@ class Segment2D {
     Segment_2 _seg;
 };
 
+
 class Polygon2D {
   public:
     Polygon2D(Polygon_2 p) : _pol(p) {}
@@ -42,7 +43,9 @@ class Polygon2D {
     Polygon_2 _pol;
 };
 
+
 Polygon2D refinement_by(Polygon2D &p, K::FT delta);
+
 
 std::ostream& operator<<(std::ostream &os, const Point_2 &p);
 std::ostream& operator<<(std::ostream &os, const Segment2D &seg);

### 2018-04-27 presentation/main.tex
Presentation skeleton
We need data obviously but here is the skeleton of our presentation. Pretty easy.

\documentclass[draft]{beamer}

\usetheme{Pittsburgh}
\usecolortheme{dove}

\usepackage[]{amsmath}
\usepackage{amssymb}
\usepackage{cmbright}
\usepackage{bm}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\abs}[1]{|#1|}
\newcommand{\set}[1]{\{ #1 \}}
\newcommand{\defkey}{\textbf}

\title{Measuring polygonal ``niceness''}
\author[Duppala, Kraemer]{%
Sharmila Duppala\inst{1}, %
David Kraemer\inst{1}}

\institute[Stony Brook University]
{
  \inst{1}%
  AMS 545: Computational Geometry \\
  Stony Brook University
}

\date[2018]{May 1, 2018}

\begin{document}

\frame{\titlepage}

\begin{frame}[t]{Preliminaries}
  \begin{itemize}
    \item $\lambda(A)$ is the area of a set $A \subseteq \RR^2$.
    \item Let $P \subseteq \RR^2$ denote a simple bounded closed polygon.
    \item $\partial P$ is the boundary of $P$.
    \item $[x,y]$ is the closed line segment bounded by $x,y \in \RR^2$.
  \end{itemize}
\end{frame}

\begin{frame}[t]{Measures of ``niceness''}
  \begin{definition}[$\alpha$-fatness]
    The \defkey{$\bm{\alpha}$-fatness score} is given by
    \begin{equation*}
      \alpha(P) = \inf\set{
        \frac{\lambda(B(x, \rho) \cap P)}{\lambda(B(x, \rho))} :
        x \in \partial P, \rho > 0, P \not\subseteq B(x, \rho)
      }
    \end{equation*}
  \end{definition}
  \begin{itemize}
    \item For every point $x \in \partial P$, sweep through all balls of radius
      $\rho$, centered at $x$, that don't contain $P$.
    \item Compute the proportion of area covered by both $P$ and $B(x,\rho)$.
    \item Find the smallest such proportion. This is $\alpha(P)$.
    \item It's much easier when the ball is a square!
  \end{itemize}
\end{frame}

\begin{frame}[t]{Measures of ``niceness''}
  \begin{definition}[Chord-area]
    The \defkey{chord-area score} is given by
    \begin{equation*}
      s_\lambda(P) =
      \inf_{x,y \in \partial P} \max( \lambda(P'), \lambda(P'')),
    \end{equation*}
    where the chord $[x,y]$ partitions $P = P' \cup P''$.
  \end{definition}
  \begin{itemize}
    \item This is a ``minimax''-esque definition. We want the least bad resulting split.
  \end{itemize}
\end{frame}

\begin{frame}[t]{Implementation}
  \begin{itemize}
    \item The measurements were implemented in C++ using CGAL with exact
      arithmetic kernel.
    \item We used a $\delta$-boundary discretizing scheme: the length of $[x_k,
      x_{k+1}]$ is at most $\delta > 0$ for consecutive boundary vertices.
    \item Generating useful test polygons was tricky.
    \item We ran our measurements on [THESE CLASSES OF POLYGONS].
  \end{itemize}
\end{frame}

\begin{frame}[t]{Results}

\end{frame}

\end{document}

### 2018-05-04 polygonal-niceness/generators.cpp
Some final changes to the code

@@ -1,0 +1,24 @@
+#include "generators.h"
+#include "io_utils.h"
+
+std::function<Polygon2D(int)> mitchell_polygons(int type, int start, int stop, bool smoothed)
+{
+  auto polygons = read_mitchell_data(type, start, stop, smoothed);
+
+  return [=](int n) 
+  {
+    std::cout << "Computing polygon #" << n << " in Mitchell (" << type << "," << start;
+    std::cout << "," << stop << ") " << (smoothed ? "" : "un") << "smoothed." << std::endl;
+    return polygons[n-1]; 
+  };
+}
+
+std::function<Polygon2D(int)> usa_polygons()
+{
+  auto polygons = read_usa_data();
+
+  return [=](int n)
+  {
+    return polygons[n];
+  };
+};

### 2018-05-04 polygonal-niceness/generators.h

@@ -1,0 +1,11 @@
+#ifndef _GENERATORS_H
+#define _GENERATORS_H
+
+#include "kernel_specs.h"
+#include "polygon2d.h"
+
+std::function<Polygon2D(int)> mitchell_polygons(int type, int start, int stop, bool smoothed);
+
+std::function<Polygon2D(int)> usa_polygons();
+
+#endif

### 2018-05-04 polygonal-niceness/io_utils.cpp

@@ -1,6 +1,145 @@
 #include "io_utils.h"
 
 
+#include <sstream>
+
+
+char usps_abbrevs[56][3] = { 
+  "ak", "al", "ar", "as", "az", "ca", "co", "ct", 
+  "dc", "de", "fl", "ga", "gu", "hi", "ia", "id", 
+  "il", "in", "ks", "ky", "la", "ma", "md", "me", 
+  "mi", "mn", "mo", "mp", "ms", "mt", "nc", "nd", 
+  "ne", "nh", "nj", "nm", "nv", "ny", "oh", "ok", 
+  "or", "pa", "pr", "ri", "sc", "sd", "tn", "tx", 
+  "ut", "va", "vi", "vt", "wa", "wi", "wv", "wy"
+};
+
+
+
+std::string usps_id(int n)
+{
+  return std::string(usps_abbrevs[n]);
+}
+
+
+std::vector<Polygon2D> read_mitchell_data(int n, int start, int stop, bool smoothed)
+{
+  auto input_dir = std::string("data/input/mitchell_polygons/");
+  input_dir += std::to_string(n);
+  input_dir += std::string("/");
+  bool data_row = false;
+
+  std::cout << "Reading from '" << input_dir << "':" << std::endl;
+
+  std::vector<Polygon2D> polygons;
+
+  for (int i = start; i < stop; i++)
+  {
+
+    std::vector<Point_2> poly;
+
+    std::string filename = input_dir;
+    std::cout << "\t" << input_dir << i << (smoothed? "s.poly" : ".poly") << " ... ";
+    std::ifstream infile(input_dir + std::to_string(i) + std::string(smoothed? "s.poly" : ".poly"));
+    if (!infile)
+    {
+      std::cerr << " failure!" << std::endl;
+      std::abort();
+    }
+    std::cout << " success!" << std::endl;
+
+
+    std::string line;
+
+    data_row = false;
+    while (std::getline(infile, line))
+    {
+      // skip the first row, it's not important
+      if (!data_row)
+      {
+        data_row = true;
+        continue;
+      }
+
+      std::stringstream stream;
+      stream << line;
+      K::FT x, y;
+      stream >> x >> y;
+      poly.push_back(Point_2(x,y));
+      stream.str("");
+    }
+
+    polygons.push_back(
+        Polygon_2(
+          poly.data(),
+          poly.data() + poly.size()
+          )
+        );
+  }
+
+  return polygons;
+
+}
+
[…]

### 2018-05-04 polygonal-niceness/io_utils.h

@@ -12,6 +12,9 @@
 #include "polygon2d.h"
 
 
+std::vector<Polygon2D> read_mitchell_data(int n, int start, int stop, bool smoothed);
+std::vector<Polygon2D> read_usa_data();
+
 std::vector<std::vector<K::FT>> generate_data(
     std::function<Polygon2D(int)> poly_generator,
     std::tuple<const int, const int, const int> n_range,
@@ -20,7 +23,7 @@ std::vector<std::vector<K::FT>> generate_data(
 
 void write_data(
     std::vector<std::vector<K::FT>> data, 
-    std::vector<std::string> header,
+    std::tuple<const K::FT, const K::FT, const int> delta_linspace,
     std::string output_file);
 
 #endif

### 2018-05-04 polygonal-niceness/kernel_specs.h

@@ -15,4 +15,5 @@ typedef CGAL::Polygon_2<K> Polygon_2;
 typedef CGAL::Polygon_with_holes_2<K> Polygon_with_holes_2;
 
 
+
 #endif 

### 2018-05-04 polygonal-niceness/main.cpp

@@ -3,27 +3,73 @@
 #include "niceness_functions.h"
 #include "io_utils.h"
 #include "measurements.h"
+#include "generators.h"
 
 
 int main()
 {
-  auto p = square_of_length(12);
-  std::cout << p << std::endl;
-  auto q = refinement_by(p, 4);
-  std::cout << q << std::endl;
 
-  // auto data = generate_data(
-  //     generator,
-  //     std::make_tuple(3,103,1),
-  //     std::make_tuple(1e-4,1e-3,3),
-  //     alpha_fatness);
+  auto generator = usa_polygons();
+  auto measurement = chord_arc_infinity;
+  std::string measure = "chord_arc_infinity";
 
-  // std::vector<std::string> header {"n","1e-4","5e-4","1e-3"};
+  std::cout << "Running data generation on USA state shape polygons." << std::endl;
 
-  // write_data (
-  //     data,
-  //     header,
-  //     "data/regular_ngon_alpha_fatness_scores.csv");
+  auto deltas = std::make_tuple(K::FT{1}, K::FT{1}, 1);
+
+  std::cout << "Generating data..." << std::endl;
+  auto data = generate_data(
+      generator,
+      std::make_tuple(1,2,1),
+      deltas,
+      measurement);
+  std::cout << "Success!" << std::endl;
+
+  std::string output = "data/output/us/";
+  output += "us_states_" + measure +  ".csv";
+
+  std::cout << "Writing data to file..." << std::endl;
+  write_data(
+      data,
+      deltas,
+      output);
+  std::cout << "Success!" << std::endl;
+
+
+  
+
+
+  //int set, start, stop;
+  //bool smoothed;
+
+  //auto measurement = alpha_fatness_score;
+  //std::string measure = "alpha_score";
+
+  //std::cout << "Running data generation on Professor Mitchell's polygons." << std::endl;
+  //std::cout << "Which data set? ";
+  //std::cin >> set >> start >> stop >> smoothed;
+  //std::cout << std::endl;
+  //auto generator = mitchell_polygons(set, start, stop, smoothed);
+
+  //auto deltas = std::make_tuple(K::FT{0.05}, K::FT{1.0}, 3);
+
+  //std::cout << "Generating data..." << std::endl;
+  //auto data = generate_data(
+  //    generator,
+  //    std::make_tuple(start,stop,1),
+  //    deltas,
+  //    measurement);
+  //std::cout << "Success!" << std::endl;
+
[…]

### 2018-05-04 polygonal-niceness/measurements.h

@@ -4,11 +4,40 @@
 
 #include "kernel_specs.h"
 #include "polygon2d.h"
+#include "niceness_functions.h"
 
-
-std::function<K::FT(Polygon2D)> farea = [](Polygon2D p) {
+std::function<K::FT(Polygon2D)> farea = [](Polygon2D p)
+{
   return p.area();
 };
+
+std::function<K::FT(Polygon2D)> infinity_perim = [](Polygon2D p)
+{
+  return p.infinity_perimeter();
+};
+
+std::function<K::FT(Polygon2D)> one_perim = [](Polygon2D p)
+{
+  return p.one_perimeter();
+};
+
+std::function<K::FT(Polygon2D)> chord_area = [] (Polygon2D p)
+{
+  return chord_f_score(p, farea) / p.area();
+};
+
+std::function<K::FT(Polygon2D)> chord_arc_infinity = [] (Polygon2D p)
+{
+  return chord_f_score(p, infinity_perim) / p.infinity_perimeter();
+
+};
+
+std::function<K::FT(Polygon2D)> chord_arc_one = [] (Polygon2D p)
+{
+  return chord_f_score(p, one_perim) / p.one_perimeter();
+
+};
+
 
 std::function<K::FT(Polygon2D)> alpha_fatness = alpha_fatness_score;
 
@@ -21,5 +50,6 @@ Polygon2D square_of_length(int n)
   points[3] = Point_2(0,n);
   return Polygon2D(Polygon_2(points, points+4));
 }
+
 
 #endif

### 2018-05-04 polygonal-niceness/polygon2d.cpp

@@ -3,6 +3,7 @@
 
 #include <CGAL/squared_distance_2.h>
 #include <CGAL/Boolean_set_operations_2.h>
+#include <CGAL/number_utils.h> 
 
 
 #include <vector>
@@ -13,17 +14,30 @@
 void _compute_edge_refinement(Point_2 source, Point_2 target, K::FT delta, std::vector<Point_2> &points);
 
 
+K::FT _norm_one(K::FT x, K::FT y)
+{
+  return CGAL::abs(x) + CGAL::abs(y);
+}
+
+K::FT _norm_inf(K::FT x, K::FT y)
+{
+  return std::max(CGAL::abs(x), CGAL::abs(y));
+}
+
+
 bool Polygon2D::is_refined_by(K::FT delta)
 {
   auto delta_sqr = delta * delta;
-  auto origin = _pol[0];
-  auto current = origin;
-  auto next = origin;
+  Point_2 curr, next;
+
 
   for (unsigned int i = 0; i < _pol.size(); i++)
   {
+    curr = _pol[i];
     next = _pol[(i+1) % _pol.size()];
-    auto dist_sqr = CGAL::squared_distance(current, next);
+    
+    auto dist_sqr = CGAL::squared_distance(curr, next);
+
     if (delta_sqr < dist_sqr)
     {
       return false;
@@ -33,10 +47,46 @@ bool Polygon2D::is_refined_by(K::FT delta)
   return true;
 }
 
+K::FT Polygon2D::infinity_perimeter()
+{
+  std::function<K::FT(K::FT,K::FT)> l_inf = _norm_inf;
+  return _norm_perimeter(l_inf);
+}
+
+K::FT Polygon2D::one_perimeter()
+{
+  std::function<K::FT(K::FT,K::FT)> l_one = _norm_one;
+  return _norm_perimeter(l_one);
+}
+
+K::FT Polygon2D::_norm_perimeter(std::function<K::FT(K::FT,K::FT)> norm)
+{
+  K::FT perimeter {0};
+  auto start = _pol.edges_circulator();
+
+  if (start != 0) // check for null polygons
+  {
+    auto current = start;
+    do
+    {
+      auto edge = *current;
+      auto x_disp = edge.target().x() - edge.source().x();
+      auto y_disp = edge.target().y() - edge.source().y();
+
+      perimeter += norm(x_disp, y_disp);
+
+    } while (current != start);
+
+  }
+
+  return perimeter;
+
[…]

### 2018-05-04 polygonal-niceness/polygon2d.h

@@ -24,6 +24,8 @@ class Polygon2D {
 
     bool is_refined_by(K::FT delta);
     K::FT area() { return _pol.area(); }
+    K::FT infinity_perimeter();
+    K::FT one_perimeter();
     bool is_convex() { return _pol.is_convex(); }
     bool is_simple() { return _pol.is_simple(); }
     int size() const { return _pol.size(); }
@@ -41,6 +43,9 @@ class Polygon2D {
     Point_2 operator[](int index) const { return _pol[index]; }
     
     Polygon_2 _pol;
+
+  private:
+    K::FT _norm_perimeter(std::function<K::FT(K::FT,K::FT)> norm);
 };
 
 

### 2018-05-04 polygonal-niceness/predicates.cpp

@@ -17,7 +17,6 @@ bool is_chord(int i, int j, Polygon2D &p)
          )
        )
     {
-      std::cout << "(" << k << "," << m << ")" << std::endl;
       if (intersect(Segment2D(p[i],p[j]), Segment2D(p[k], p[m])))
       {
         return false;

### 2018-05-04 presentation/main.tex
Presentation

@@
-\documentclass[draft]{beamer}
+\documentclass[]{beamer}
 
@@
 \usepackage{cmbright}
+\usepackage[]{graphicx}
 \usepackage{bm}
@@
 
-\title{Measuring polygonal ``niceness''}
+\title{Measuring polygonal niceness}
 \author[Duppala, Kraemer]{%
@@
     \item $\partial P$ is the boundary of $P$.
+    \item $\abs{\partial P}$ is the perimeter of $P$.
     \item $[x,y]$ is the closed line segment bounded by $x,y \in \RR^2$.
@@
 
-\begin{frame}[t]{Measures of ``niceness''}
+\begin{frame}[t]{Measures of niceness}
   \begin{definition}[$\alpha$-fatness]
@@
       \alpha(P) = \inf\set{
-        \frac{\lambda(B(x, \rho) \cap P)}{\lambda(B(x, \rho))} :
-        x \in \partial P, \rho > 0, P \not\subseteq B(x, \rho)
+        \frac{\lambda(B(x, \rho) \cap P)}{\lambda(B(x, \rho))} : \rho > 0
       }
     \end{equation*}
+    where $x \in P$, and $B(x,\rho)$ is a ball centered at
+    $x$ not containing $P$.
   \end{definition}
   \begin{itemize}
-    \item For every point $x \in \partial P$, sweep through all balls of radius
-      $\rho$, centered at $x$, that don't contain $P$.
-    \item Compute the proportion of area covered by both $P$ and $B(x,\rho)$.
+    \item The ``minimizing'' ball might contain $P$.
     \item Find the smallest such proportion. This is $\alpha(P)$.
@@
 
-\begin{frame}[t]{Measures of ``niceness''}
-  \begin{definition}[Chord-area]
-    The \defkey{chord-area score} is given by
+\begin{frame}[t]{Measures of niceness}
+  \begin{itemize}
+    \item Let $R$ be a rectangle with length $\ell$ and height $h$. (WLOG, $\ell
+      \geq h$.) Then
       \begin{equation*}
-      s_\lambda(P) =
-      \inf_{x,y \in \partial P} \max( \lambda(P'), \lambda(P'')),
+        \alpha(R) = \frac{h}{4\ell}.
+      \end{equation*}
+  \end{itemize}
+  \begin{center}
+    \includegraphics[width=0.55\textwidth]{../plots/alpha_fatness_rectangle.eps}
+  \end{center}
+\end{frame}
+
+\begin{frame}[t]{Measures of niceness}
+  \begin{itemize}
+    \item Let $C$ be a circle with radius $r$. Then 
+      \begin{equation*}
+        \alpha(C) = \frac{\pi r^2}{16r^2} = \frac{\pi}{16} < \frac{1}{4}.
+      \end{equation*}
+  \end{itemize}
+  \begin{center}
+    \includegraphics[width=0.55\textwidth]{../plots/alpha_fatness_circle.eps}
+  \end{center}
+\end{frame}
+
+\begin{frame}[t]{Measures of niceness}
+  \begin{definition}[Chord-arc]
+    The \defkey{chord-arc score} is given by
+    \begin{equation*}
+      s_p (P) =
+      \inf\set{\max( \abs{\partial P'}, \abs{\partial P''}): x,y \in \partial P},
     \end{equation*}
@@
   \begin{itemize}
-    \item This is a ``minimax''-esque definition. We want the least bad resulting split.
+    \item This is a ``minimax'' definition. We want the least bad resulting split.
+    \item The polygon perimeter is computed by summing the ``lengths'' of each
+      boundary edge.
+    \item Here $p$ indicates a norm. Ideally $p = 2$, but for computation
+      purposes we choose $p = 1$ or $p= \infty$.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[t]{Measures of niceness}
+  \begin{itemize}
+    \item Let $R$ be a rectangle with length $\ell$ and height $h$. (WLOG, $\ell
+      \geq h$.) Then
+      \begin{equation*}
+        s_p(R) = 2h + \ell
+      \end{equation*}
+  \end{itemize}
+  \begin{center}
+    \includegraphics[width=0.65\textwidth]{../plots/chord_arc_rectangle.eps}
+  \end{center}
+  \begin{itemize}
+    \item This holds for many $p$.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}[t]{Stray observations}
+  \begin{itemize}
+    \item The $\alpha$ fatness score seems to penalize oblong polygons and
+      reward ``squarely compact'' polygons.
+    \item The chord-arc score seems to penalize local nonconvexity. 
+    \item Remember that we want a large $\alpha$ score but a small chord-arc
+      score.
   \end{itemize}
@@
     \item Generating useful test polygons was tricky.
-    \item We ran our measurements on [THESE CLASSES OF POLYGONS].
+    \item We ran our measurements on
+      \begin{itemize}
+        \item Special internally generated nice polygons,
+        \item Randomly generated ``typical'' polygons (courtesy of Professor
+          Mitchell),
+        \item (Simplified) US state boundaries.
+      \end{itemize}
   \end{itemize}
@@
 
-\begin{frame}[t]{Results}
+\begin{frame}[t]{Randomly generated polygons} 
+  \includegraphics[width=\textwidth]{../plots/u_100_alpha_score_chord_arc_infinity_vertices_0-05_delta_ranking.eps}
+  ($\delta  = 0.05$)
+\end{frame}
 
+\begin{frame}[t]{Randomly generated polygons}
+  \includegraphics[width=\textwidth]{../plots/u_100_chord_arc_one_chord_arc_infinity_vertices_0-05_delta_ranking.eps}
+  ($\delta  = 0.05$)
 \end{frame}

### 2018-05-04 paper/main.tex
Draft report with all of the LaTeX stuff

\documentclass[draft]{jocg}

\usepackage{amsmath,amsfonts}
\usepackage{amsthm}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage[mathlines]{lineno}
\linenumbers

\usepackage[
  backend=biber,
  style=alphabetic,
  sorting=ynt
]{biblatex}
\addbibresource{main.bib}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\EE}{\mathcal{E}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\abs}[1]{|#1|}
\newcommand{\chordarc}{s_{\abs{\partial~\cdot~}}}
\DeclareMathOperator{\diam}{\mathrm{diam}}
\DeclareMathOperator{\conv}{\mathcal{}}

\newtheorem{proposition}{Proposition}[section]

\theoremstyle{definition}
\newtheorem{definition}[proposition]{Definition}

\theoremstyle{remark}
\newtheorem{remark}[proposition]{Remark}

\title{%
  \MakeUppercase{Measuring polygonal niceness}%
  \thanks{%
    This paper comprises the completion of the final project for AMS 545
    ``Computational Geometry''.
  }
}

\author{%
  Sharmila~Duppala%
  \thanks{%
    \affil{Department of Computer Science}, 
    \email{sduppala@cs.stonybrook.edu}%
  }\, and
  David~Kraemer.%
  \thanks{%
    \affil{Department of Applied Mathematics},
    \email{david.kraemer@stonybrook.edu}%
  }
}

\begin{document}

\maketitle

\begin{abstract}
  In which I do all of the work and my partner free loads on literally every
  piece of this project.
\end{abstract}

\tableofcontents

\section{Introduction}

\begin{enumerate}
  \item Paragraph introducing general problem
  \item Paragraph on applications to gerrymandering problems.
  \item Paragraph explaining the limitations of this application. (Perhaps this
    should be in the discussion?)
  \item Paragraph outlining the paper.
\end{enumerate}

\section{Theoretical background}

The area of a subset $S \subseteq \RR^2$ of the plane is denoted by
$\lambda(S)$. We will denote the boundary of $S$ by $\partial S$. For two points
$x,y \in \RR^2$, the closed line segment with endpoints in $x$ and $y$ is
denoted $[x,y]$. For $p \in [1, \infty]$, we define the $p$-ball as $B_{p}(x,
\varepsilon) = \set{y \in \RR^2 : \norm{x-y}_p \leq \varepsilon}$ and we will
only be interested in the closed case. Unless otherwise stated, we shall operate
in the Euclidean world with $p = 2$. Throughout we shall assume that $P
\subseteq \RR^2$ is a simple bounded closed polygon. The class of such polygons
is given by $\PP$. Its perimeter is denoted by $\abs{\partial P}$.

\subsection{The $\alpha$-fatness score}

One approach to measuring the relative ``fatness'' of a polygon seeks to
identify regions of the shape which behave highly unlike balls.

\begin{definition}
  The $\alpha$-fatness score of a polygon $P$ is given by
  \begin{equation*}
    \alpha(P) = \inf\set{\frac{\lambda[P \cap B(x,
    \varepsilon)]}{\lambda[B(x,\varepsilon)]} : \varepsilon > 0, x \in P}
  \end{equation*}
  where we impose that the ball $B(x,\varepsilon)$
  does not contain $P$. 
  \label{def:alpha}
\end{definition}

The constraint that $P \not\subseteq B(x,\varepsilon)$ ensures definiteness:
otherwise, let $\varepsilon \to \infty$ and the ratio $\frac{\lambda[P \cap B(x,
\varepsilon)]}{\lambda[B(x, \varepsilon)]}$ always approaches $0$. An intuition
for $\alpha(P)$ emerges from considering how it behaves on balls.

\begin{proposition}
  For any $P$, $\alpha(P) \leq \frac{1}{4}$, and if $P = B(x_0, r)$
  then we have equality.
  \label{prop:alpha}
\end{proposition}

\begin{proof}
  To show that $\alpha(P) \leq \frac{1}{4}$, it suffices to show only for convex
  $P$, because $P \subseteq \conv(P)$ implies $\lambda[P \cap B(x, \varepsilon)]
  \leq \lambda[\conv(P) \cap B(x, \varepsilon)]$. Let $d = \diam (P)$ and fix
  $x,y \in \partial P$ such that $\abs{[x,y]} = d$. Assume without loss of
  generality that $x$ lies above $y$, and consider the ball $B(x, d)$. Then $P$
  does not meet the upper disk of $B(x,d)$, for otherwise we could choose $z \in
  P$ in the upper disk of $B(x,d)$ which forms a chord of $P$ longer than $d$.
  A similar argument shows that $P$ cannot occupy more than half of the lower
  disk of $B(x,d)$. Hence
  \begin{equation*}
    \alpha(P) \leq \frac{\lambda[P \cap B(x,d)]}{\lambda[B(x,d)]} \leq
    \frac{1}{4},
  \end{equation*}
  as needed.

  The fact that $\alpha(B(x_0, r)) = \frac{1}{4}$ relies on a neat
  result \cite{10.2307/30044198} that shows that the $L_p$
  ellipsoid $\EE$ with radii $a, b$ has area
  \begin{equation*}
    \lambda(\EE) = a b \cdot 4
    \frac{\Gamma(1+\frac{1}{p})^2}{\Gamma(1+\frac{n}{p})}.
  \end{equation*}
  In our case, $\alpha(B(x_0, r))$ is achieved at a ball on a ``corner'' point
  with radius $2r$.
\end{proof}

Hence, the $\alpha$-score is greater for polygons which exhibit ``niceness''
characteristics. It is not affected tremendously by local nonconvexity in $P$ so
long as $P$ ``snugly fits'' into a ball shape, which is a global property.

\subsection{The chord-$f$ score}

A different class of ``fatness'' measures arises through partitioning $P$ into
two (interior disjoint) polygons $P = P' \cup P''$ via chords. A chord is a pair
$x,y \in \partial P$ such that the segment $[x,y]$ is contained in the interior
of $P$ except at the endpoints $x$ and $y$. Such a chord defines a partition of
$P = P' \cup P''$ by orientation, so that $\partial P'$ is the arc from $x$ to
$y$ together with $[x,y]$ and that $\partial P''$ is the arc from $y$ to $x$
together with $[x,y]$.

\begin{definition}
  Let $f : \mathcal{P} \to \RR$. For a given $P \in \mathcal{P}$, its
  \emph{chord-$f$ score} is given by
  \begin{equation*}
    s_f (P) = \inf \set{\max(f(P'), f(P'')) : x, y \in \partial P}
  \end{equation*}
  where the chord $[x,y]$ partitions $P = P' \cup P''$.
  \label{def:chord-f}
\end{definition}

The intuition for $f$ is some global measure of ``cost'' associated with respect
to $P$. For example, if $f(P) = \abs{\partial P}$, then $s_f$ identifies the
partition (or limiting sequence of partitions) which minimizes the maximum
subpolygon perimeter. Indeed, measures such as perimeter or area are the typical
choices of $f$, but any suitable property of $P$  may be employed.

The chord-$f$ score can be understood relatively simply in the context of a
minimax game. Max, given a polygon with a chord partitioning it, always chooses
the subpolygon associated with a greater $f$ (i.e., the worst cost of the
partition). Min, who plays first, tries to find a chord with the least-bad worst
cost with respect to $f$.

The member of this class of scores under this present investigation is
$\chordarc$, the so-called \emph{chord-arc} score. It is important to note that
the length of the chord $[x,y]$ which partitions $P$ is included in the
estimation of $\chordarc$. One implication of this is that the chord-arc score
need not be bounded above by $\frac{\abs{\partial P}}{2}$.  We have several
facts about $\chordarc$ which develop further intuition for the score.
\begin{proposition}
  \begin{enumerate}
    \item Let $R$ be a rectangle with height $h$ and length $\ell$. Assume that
      $h \leq \ell$. Then $\chordarc(R) = 2h + \ell$.
    \item Let $P$ be convex with perimeter $\abs{\partial P} = w$. Then
      $\chordarc(P) \leq \frac{w}{2} + \diam (P)$.
    \item Let $C$ be a circle with ``perimeter'' $2\pi r$. Then $\chordarc(C) =
      (\pi + 2)r$.
  \end{enumerate}
  \label{rem:chordarc}
\end{proposition}

\begin{proof}
  \begin{enumerate}
    \item That the optimal partition bisects $R$ is readily apparent,
      for this minimizes the maximum perimeter length of either sub-rectangle.
      A case analysis confirms that the preferred strategy for Min is to choose
      a chord along the smaller dimension (i.e., $h$) to bisect $R$, and in this
      case the maximum arc length is $2h + 2\left( \frac{\ell}{2} \right) = 2h +
      \ell$, as needed.
    \item For $P$ convex, a perimeter-bisecting chord, whose length is at most
      $\diam(P)$, always exists. 
    \item This follows from part 2 by noticing that the length of \emph{any}
      perimeter-bisecting chord is $\diam(C) = 2r$. \qedhere
  \end{enumerate}
\end{proof}

\section{Overview of empirical design}

\begin{enumerate}
  \item Paragraph explaining discretization procedure.
  \item Pseudocode and explanation for the alpha fatness.
  \item Pseudocode and explanation for the chord $f$ score.
  \item Formulate ``random'' polygons.
  \item Explain U.S. state boundary data collection.
\end{enumerate}

\section{Empirical results}

\begin{enumerate}
  \item Show how changing $\delta$ affects scores.
  \item Compare scores (by ranking) on random polygons.
  \item Compare scores (by ranking) on U.S. state boundary data.
\end{enumerate}

\section{Discussion}

\begin{enumerate}
  \item Comment on the results.\cite{cgal:eb-18a}
  \item Talk about applications to Gerrymandering.\cite{cgal:gw-p2-18a}
\end{enumerate}

\medskip

\printbibliography[heading=bibintoc]

\end{document}

### 2018-05-04 paper/main.tex
Changed some stuff
Updates to the paper.
Section 3 is done, section 4 is almost done. I am just generating some final plots and putting them into the paper. Then the only things that remain are the introduction and conclusion sections.

@@
-\documentclass[draft]{jocg}
+\documentclass[]{jocg}
 
@@
 \usepackage[mathlines]{lineno}
+\usepackage[]{graphicx}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 \linenumbers
@@
 \begin{abstract}
-  In which I do all of the work and my partner free loads on literally every
-  piece of this project.
 \end{abstract}
@@
 
-\begin{enumerate}
-  \item Paragraph explaining discretization procedure.
-  \item Pseudocode and explanation for the alpha fatness.
-  \item Pseudocode and explanation for the chord $f$ score.
-  \item Formulate ``random'' polygons.
-  \item Explain U.S. state boundary data collection.
-\end{enumerate}
+In principal of computing the $\alpha$ and chord-$f$ scores relies on sweeping
+the continuum of points of $P$ and evaluating the aforementioned measurements.
+To estimate this process in practice, we employ the following discretizing
+scheme. Let $P$ be determined by the vertices $[v_1, \dots, v_n]$ given in
+counterclockwise order. Then, given $\delta > 0$, loop through the vertices of
+$P$, checking if $\norm{v_{i+1} - v_i} > \delta$. In the case where this holds,
+we insert $v_i' = \frac{v_i + v_{i+1}}{2}$ after $v_i$ into the polygon and
+resume the loop. This ensures that for any two adjacent vertices $v_{i}$ and
+$v_{i+1}$ in the representation of $P$ we have $\norm{v_{i+1} - v_i} \leq
+\delta$. As $\delta \to 0$ this estimates $\partial P$ more exactly. All
+computations are done with respect to the $L_{\infty}$ norm. The implementation
+of this procedure is given in Algorithm \ref{alg:delta}.
+
+%% Pseudocode for the delta refinement
+
+\begin{algorithm}[h]
+  \begin{algorithmic}[0]
+    \Procedure{RefineBy}{$P,\delta$}
+    \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
+    \State{$v = v_1$}
+    \While {$\textit{next}(v) \ne v_1$}
+    \If {$\norm{\textit{next}(v) - v}_2 > \delta$}
+      \State{\textrm{Insert $\textit{midpoint}(v, \textit{next}(v))$ into $P$
+      after $v$}} 
+      \Comment{Now $\textit{next}(v)$ is the midpoint}
+      \EndIf
+      \EndWhile
+      \EndProcedure
+    \end{algorithmic}
+    \label{alg:delta}
+\end{algorithm}
+
+Given a $\delta$-refined polygon $P$, the computation of $\alpha(P)$ is
+relatively straightforward, with the simplification that points $x$ on which the
+ratio is computed lie on $\partial P$. The computation steps through $[v_1,
+\dots, v_n]$ and for each $v_i$ the radius $\varepsilon$ of the
+minimum-enclosing $\infty$-ball centered at $v_i$ is computed. Then for
+$\varepsilon_k = \frac{k}{100} \varepsilon$, $k = 1, \dots, 100$, the ratio 
+\begin{equation*}
+  \frac{\lambda[P \cap B_{\infty}(v_i, \varepsilon_k)]}{B_{\infty}(v_i,
+  \varepsilon_k)}
+\end{equation*}
+is computed and the smallest such ratio is kept. The minimum over all $v_i$ is
+given as $\alpha(P)$. The implementation of the $\alpha$ score is given in
+Algorithm \ref{alg:alpha}.
+
+%% Pseudocode for the alpha score
+
+\begin{algorithm}[h]
+  \begin{algorithmic}[0]
+    \Function{$\alpha$Score}{$P$}
+    \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
+    \State{$\textrm{min} = \infty$}
+    \For {$v \in P$}
+    \State{$\varepsilon = \textrm{radius of minimum enclosing ball of $P$ at
+    $v$}$}
+    \For {$k = 1, 2, \dots, 100$} \Comment{$100$ is arbitrary}
+    \State{$\varepsilon_k = \frac{k}{100} \varepsilon$}
+    \State{$\textrm{area} = \frac{\lambda[P \cap B_{\infty}(v, \varepsilon_k)]}{B_{\infty}(v, \varepsilon_k)}$}
+    \If {$\textrm{min} > \textrm{area}$}
+      \State{$\textrm{min} = \textrm{area}$}
+      \EndIf
+      \EndFor
+      \EndFor
+      \State{\Return{\textrm{min}}}
+      \EndFunction
+    \end{algorithmic}
+  \label{alg:alpha}
+\end{algorithm}
+
+Similarly, given a $\delta$-refined polygon $P$, the chord-$f$ score is computed
+by sweeping all possible chords of $P$. For each point $v_i, v_j \in \partial P$
+with $i < j$, if $[v_i, v_j]$ is indeed a valid chord of $P$, the partition $P =
+P' \cup P''$ is computed and the maximum of $f(P')$ and $f(P'')$ is kept. The
+minimum such value is given as $s_f(P)$. The implementation of the chord-$f$
+score is given in Algorithm \ref{alg:chordf}.
+
+%% Pseudocode for the chord f score
+
+\begin{algorithm}[h]
+\begin{algorithmic}[0]
+  \Function{ChordScore}{P,f}
+  \State{$P = [v_1, v_2, v_3, \dots, v_n]$};
+  \For {$v \in P$}
+  \For {$w \in [\textit{next}(v), \dots, v_n]$}
+  \If {$[v,w]$ is a chord of $P$}
+    \State{Partition $P = P' \cup P''$ by $[v,w]$}
+    \State{$\textrm{submax} = \textit{max}(f(P'), f(P''))$}
+    \If {$\textrm{min} > \textrm{submax}$}
+      \State{$\textrm{min} = \textrm{submax}$}
+      \EndIf
+    \EndIf
+  \EndFor
+  \EndFor
+  \State{\Return{\textrm{min}}}
+  \EndFunction
+\end{algorithmic}
+\label{alg:chordf}
+\end{algorithm}
+
+All of these algorithms are implemented in CGAL \cite{cgal:eb-18a} with the
+extensive use of the 2D Polygon library \cite{cgal:gw-p2-18a}.
 
 \section{Empirical results}
+
+We evaluate our measurements on randomly generated polygons with vertices in the
+unit square $[0,1] \times [0,1]$. We consider collections of such polygons of
+10, 50, and 100 vertices. In Figure \ref{fig:delta}, we measure the effect of
+sweeping $\delta$ between $0.05$ and $1$ on the resulting measurements. Figure
+\ref{fig:alph-inft-10} shows a comparison of $\alpha$-fatness and
+${\chordarc}_{\infty}$ scores for polygons on 10 vertices. Figure
+\ref{fig:alph-one-50} shows a similar comparison of $\alpha$-fatness and
+${\chordarc}_{1}$ scores for polygons on 50 vertices.
+
+\begin{figure}[t]
+  \centering
+  %\includegraphics{<+file+>}
+  \caption{Effect of sweeping $\delta$ on measurements}
+  \label{fig:delta}
+\end{figure}<++>
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[height=0.8\textheight]{../plots/u_10_alpha_score_chord_arc_infinity_vertices_0-05_delta_ranking.jpg}
+  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
+  generated polygons on 10 vertices.}
+  \label{fig:alph-inft-10}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[height=0.8\textheight]{../plots/u_50_alpha_score_chord_arc_one_vertices_0-05_delta_ranking.jpg}
+  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
+  generated polygons on 50 vertices.}
+  \label{fig:alph-inft-10}
+\end{figure}
 
@@
 \begin{enumerate}
-  \item Comment on the results.\cite{cgal:eb-18a}
-  \item Talk about applications to Gerrymandering.\cite{cgal:gw-p2-18a}
+  \item Comment on the results.
+  \item Talk about applications to Gerrymandering.
 \end{enumerate}

### 2018-05-04 paper/main.tex
Paper is basically done
All the pieces are there.

@@
 \usepackage[english]{babel}
+\usepackage{booktabs}
 \usepackage{mathtools}
@@
   backend=biber,
-  style=alphabetic,
+  style=nature,
   sorting=ynt
@@
 \newcommand{\abs}[1]{|#1|}
-\newcommand{\chordarc}{s_{\abs{\partial~\cdot~}}}
+\newcommand{\chordarc}{{s_{\abs{\partial~\cdot~}}}}
 \DeclareMathOperator{\diam}{\mathrm{diam}}
@@
   \thanks{%
-    This paper comprises the completion of the final project for AMS 545
+    This paper constitutes the completion of the final project for AMS 545
     ``Computational Geometry''.
@@
 
-\begin{enumerate}
-  \item Paragraph introducing general problem
-  \item Paragraph on applications to gerrymandering problems.
-  \item Paragraph explaining the limitations of this application. (Perhaps this
-    should be in the discussion?)
-  \item Paragraph outlining the paper.
-\end{enumerate}
+Convexity is from many perspectives the ``gold standard'' of niceness for planar
+subsets, because it excludes at once large classes of pathological sets
+altogether. Yet for establishing a quantitative measure of niceness that matches
+with intuitive or legal understandings, convexity is both too restrictive and too
+general. The relevant consideration at present revolves around drawing electoral
+districts. The immense political consequences of favorable (or unfavorable)
+maps has resulted in the development of creative classes of polygonal regions
+utilized for this purpose. There exists a strong civic prerogative for providing
+quantitative measures of niceness. In a concurrent opinion in the 2004 suit
+\textit{Vieth v. Jubelirer} decided by the U.S. Supreme Court, Justice Anthony
+Kennedy writes 
+\begin{quote}
+  Because, in the case before us, we have no standard by which to measure the
+  burden appellants claim has been imposed on their representational rights,
+  appellants cannot establish that the alleged political classifications burden
+  those same rights.  Failing to show that the alleged classifications are
+  unrelated to the aims of apportionment, appellants’ evidence at best
+  demonstrates only that the legislature adopted political classifications. That
+  describes no constitutional flaw, at least under the governing Fourteenth
+  Amendment standard. \cite{2004vieth}
+\end{quote}
+Ought convexity be considered as such a standard? In practice, convexity is too
+restrictive (e.g., for coastal or river borders) and too general (e.g., a tiny
+vertical strip) for this purpose.
+
+The aim of this paper is to propose several alternative measures to determine
+the niceness of polygonal regions in a quantitatively rigorous way. We introduce
+two classes of measures, the $\alpha$-score and the chord-$f$ scores, develop
+some of their basic properties, and show how they perform on simulated data. The
+$\alpha$-fatness quantifies how much a given polygon resembles a ball (with
+respect to some norm). When $f$ measures the perimeter of a polygon, the
+chord-$f$ score quantifies the extent to which ``local nonconvexity'' affects
+the distribution of the total boundary. Both measures generally reward convex
+polygons, but punish certain convex ``offenders.'' Of course, there exist
+nonconvex polygons who score well on both measures as well.
+
+This paper proceeds as follows. Section 2 provides a theoretical overview for
+the $\alpha$-fatness and chord-$f$ scores and gives preliminary results on
+simple examples. Section 3 outlines the algorithms used to perform
+discretizations and compute the $\alpha$-fatness and chord-$f$ scores. Section 4
+gives the results of numerical simulations for these measures on randomly
+generated ``typical'' polygons and provides data about the success of
+discretization. Section 5 includes a discussion of the main results of the paper
+and its implications for the electoral districting process.
+
+Source code for this project can be found at
+\url{https://github.com/DavidNKraemer/polygonal-niceness}. Documentation, cruft
+removal, and user interface improvements are presently evolving.
 
@@
 
+Depending on the relative coordinates of the vertex set compared to $\delta$,
+the worst-case runtime of refinement varies. In the case where the maximum
+distance is $\delta K$, the refinement adds $O(\lg^2 K)$ vertices between the
+two coordinates. The overall runtime is $O(n \lg^2 K)$ and the total quantity of
+vertices after refinement is $O(n + n\lg^2 K)$.
+
 %% Pseudocode for the delta refinement
@@
 \begin{algorithm}[h]
-  \begin{algorithmic}[0]
+  \begin{algorithmic}[1]
     \Procedure{RefineBy}{$P,\delta$}
@@
     \If {$\norm{\textit{next}(v) - v}_2 > \delta$} 
-      \State{\textrm{Insert $\textit{midpoint}(v, \textit{next}(v))$ into $P$
-      after $v$}} 
+      \State{\textrm{Insert $\textit{midpoint}(v, \textit{next}(v))$ into $P$ after $v$}} 
       \Comment{Now $\textit{next}(v)$ is the midpoint}
@@
   \end{algorithmic}
+  \caption{%
+    The procedure used to refine a given polygon $P$ by a specified $\delta >
+    0$. This modifies the existing $P$ to satisfy the regularity condition
+    that $\norm{v_{i+1} - v_i} \leq \delta$ for each adjacent vertex pair
+    $v_{i+1}, v_i$ on the discretized boundary $\partial P$.  }
   \label{alg:delta}
@@
 given as $\alpha(P)$. The implementation of the $\alpha$ score is given in
-Algorithm \ref{alg:alpha}.
+Algorithm \ref{alg:alpha}. Though we use a sweep from $k = 1, \dots, 100$, any
+suitable range may be selected as an alternative. Unfortunately, there is no
+analogous ``bisection'' technique for determining the minimizing $k$ because
+this ratio need not be monotonic. Since $P$ need not be convex, the intersection
+$P \cap B_{\infty}(v, \varepsilon_k)$ requires $O(n \log n)$ steps. For $n$
+vertices, the runtime performance is $O(n^2 \log n)$.
 
@@
 \begin{algorithm}[h]
-  \begin{algorithmic}[0]
+  \begin{algorithmic}[1]
     \Function{$\alpha$Score}{$P$}
@@
   \end{algorithmic}
+  \caption{%
+    The $\alpha$-fatness function.  }
   \label{alg:alpha}
@@
 minimum such value is given as $s_f(P)$. The implementation of the chord-$f$
-score is given in Algorithm \ref{alg:chordf}.
+score is given in Algorithm \ref{alg:chordf}. For $n$ vertices, $O(n^2)$
+potential chords are computed. To determine if a pair of vertices is a chord
+takes $O(n)$ time, which leads to an overall runtime performance of $O(n^3)$.
 
@@
 \begin{algorithm}[h]
-\begin{algorithmic}[0]
+  \begin{algorithmic}[1]
     \Function{ChordScore}{P,f}
@@
   \end{algorithmic}
+  \caption{%
+    The chord-$f$ function.   }
   \label{alg:chordf}
@@
 All of these algorithms are implemented in CGAL \cite{cgal:eb-18a} with the
-extensive use of the 2D Polygon library \cite{cgal:gw-p2-18a}.
+extensive use of the 2D Polygon library \cite{cgal:gw-p2-18a}. For our data
+generation, we make the minor modification that measured ${\chordarc}$ is the
+ratio of the actual $\chordarc$ score with the perimeter of the overall polygon.
+This changes the interpretation of some of the theoretical results from the
+previous section but allows for easier interpretation of the data.
 
@@
 unit square $[0,1] \times [0,1]$. We consider collections of such polygons of
-10, 50, and 100 vertices. In Figure \ref{fig:delta}, we measure the effect of
-sweeping $\delta$ between $0.05$ and $1$ on the resulting measurements. Figure
-\ref{fig:alph-inft-10} shows a comparison of $\alpha$-fatness and
-${\chordarc}_{\infty}$ scores for polygons on 10 vertices. Figure
-\ref{fig:alph-one-50} shows a similar comparison of $\alpha$-fatness and
-${\chordarc}_{1}$ scores for polygons on 50 vertices.
+10, 50, and 100 vertices. In Figure \ref{fig:delta-alpha} and Figure
+\ref{fig:delta-chordarc}, we measure the effect on
+polygons of 10 vertices of sweeping $\delta$ between $0.05$ and $1$ on the
+resulting measurements. Figure \ref{fig:alph-inft-10} shows a comparison of
+$\alpha$-fatness and relative ${\chordarc}_{\infty}$ scores for polygons on 10
+vertices.  Figure \ref{fig:alph-one-50} shows a comparison of $\alpha$-fatness
+and relative ${\chordarc}_1$ scores for polygons on 50 vertices. Figure
+\ref{fig:alph-inft-100} shows a comparison of $\alpha$-fatness and relative
+${\chordarc}_{\infty}$ scores for polygons on 100 vertices.
+
+Our theoretical results seem to be confirmed in that ``ball''-like polygons get
+the highest $\alpha$-scores, and it seems that polygons with fewer
+``nonconvexities'' score better on the relative ${\chordarc}_{\infty}$ measure. We
+observe an overall decline in the relative $\chordarc$ scores as the number of
+vertices of the polygons increases. This is attributed to the corresponding
+increase in the size of the underlying perimeters of each $P$. The observation
+is not shared with the $\alpha$ score, but this can be understood as a sort of
+``coastline'' phenomenon, in which polygonal perimeters increase without limit
+while the areas converge.
 
@@
   \centering
-  %\includegraphics{<+file+>}
-  \caption{Effect of sweeping $\delta$ on measurements}
-  \label{fig:delta}
-\end{figure}<++>
+  \begin{tabular}{lrrrrrrrrrr}
+    \toprule
+    $\delta$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+    \midrule
+    0.05 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.15 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.26 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.36 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.47 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.57 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.68 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.78 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    0.89 &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    1    &  0.23 &  0.21 &  0.11 &  0.039 &  0.15 &  0.038 & 0.12 &  0.10 &  0.12 &  0.13 \\
+    \bottomrule
+  \end{tabular}
+  \caption{%
+    Effect of sweeping $\delta$ on measurements of $\alpha$-score on
+    10 randomly generated polygons with 10 vertices in $[0,1]^2$.
+    Unsurprisingly, the refinement of the different polygons has no effect on
+    the $\alpha$-fatness score, since it introduces no additional area to the
+    polygon and since the ``corners'' are already present.
+  }
+  \label{fig:delta-alpha}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \begin{tabular}{lrrrrrrrrrr}
+    \toprule
+    $\delta$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+    \midrule
+    0.05  &  0.83 &  0.46 &  0.83 &  0.89 &  0.54 &  0.67 &  0.62 &  1.00 &  0.86 &  0.55 \\
+    0.15  &  0.79 &  0.90 &  0.72 &  0.60 &  0.90 &  0.67 &  0.99 &  0.83 &  0.66 &  0.90 \\
+    0.26  &  1.00 &  0.75 &  0.50 &  0.60 &  0.90 &  0.49 &  0.77 &  0.52 &  0.72 &  0.69 \\
+    0.36  &  0.89 &  1.00 &  0.50 &  0.60 &  0.52 &  0.49 &  1.00 &  0.92 &  0.74 &  0.51 \\
+    0.47  &  0.61 &  1.00 &  0.50 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    0.57  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    0.68  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    0.78  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    0.89  &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  0.24 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    1     &  0.61 &  1.00 &  0.25 &  0.75 &  0.52 &  1.00 &  1.00 &  0.62 &  1.00 &  0.51 \\
+    \bottomrule
+  \end{tabular}
+  \caption{%
+    Effect of sweeping $\delta$ on measurements of ${\chordarc}_\infty$ on
+    10 randomly generated polygons with 10 vertices in $[0,1]^2$. The overall behavior is
+    difficult to summarize.  Though one might hope that as $\delta \to 0$ we see
+    a stabilization in the chard arc score, this does not appear to occur.
+    Moreover, there does not seem to be even a monotonic evolution in the score
+    as $\delta \to 0$. This is likely due to the fact that smaller values of
+    $\delta$ permit stranger nonconvexities to emerge as viable chords.
+  }
+  \label{fig:delta-arc}
+\end{figure}
 
@@
   \includegraphics[height=0.8\textheight]{../plots/u_50_alpha_score_chord_arc_one_vertices_0-05_delta_ranking.jpg}
-  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
+  \caption{$\alpha$ scores and ${\chordarc}_{1}$ scores for randomly
   generated polygons on 50 vertices.}
-  \label{fig:alph-inft-10}
+  \label{fig:alph-one-50}
 \end{figure}
 
-\begin{enumerate}
-  \item Show how changing $\delta$ affects scores.
-  \item Compare scores (by ranking) on random polygons.
-  \item Compare scores (by ranking) on U.S. state boundary data.
-\end{enumerate}
+\begin{figure}[t]
+  \centering
+  \includegraphics[height=0.8\textheight]{../plots/u_100_alpha_score_chord_arc_infinity_vertices_0-05_delta_ranking.jpg}
+  \caption{$\alpha$ scores and ${\chordarc}_{\infty}$ scores for randomly
+  generated polygons on 100 vertices.}
+  \label{fig:alph-inft-100}
+\end{figure}
 
 \section{Discussion}
+
+We have developed two classes of measurements for determining the niceness of
+polygonal regions in the plane and established initial results, both theoretical
+and empirical, for evaluating their effectiveness. The $\alpha$-fatness measures
+the extent to which the underlying polygon resembles a ball. It rewards
+polygons which fill squarely compact regions and punishes oblong and spread out
+polygons. The chord-arc score measures the extent to which the underlying
+polygon contains significant ``local nonconvexities'' that are not well
+distributed throughout the entire polygon. Interestingly, both measures perform
+well (even optimally) on specific types of convex polygons but severely punishes
+others. We generally find that these measures conform in some sense to an
+intuitive understanding of niceness.
+
+Extensions on these measures can be examined. The connected $\alpha$-fatness
+score, for example, computes the intersection of $B(x,\varepsilon)$ with the
+connected component of $P$ containing $x$. This might prove a more reliable
+estimate of intuitive niceness than the conventional $\alpha$-fatness score,
+because it excludes components of $P$ from consideration which are close in a
+coarse sense, but not necessarily close in a topological sense. The myriad of
+possible choices from which to choose $f$ leaves open a wide space for
+exploration. A more suitable measure than simply the perimeter may emerge as a
+consequence.
+
+The next extension of this work is to apply these measures to electoral
+districts and evaluate their success at distinguishing between offending and
+``nice'' districts. Given an increasing corpus of election districts ruled out
+or struck down by constitutional grounds, it may be possible to learn a
+classification model using these measures. Alternatively, it may be discovered
+that these measures are sufficient to distinguish between offending and nice
+districts in an unsupervised fashion.
+
+Whether quantitative measures that conform to intuitive understandings of
+niceness is relevant to crafting electoral districts at all remains an open
+question. General compactness and contiguity are only part of the requirements
+which an electoral district must satisfy under the present regime, whereas
+others, such as those given in the 1965 Voting Rights Act, bear less consequence
+from the pure shape of the district. Doubtless these quantitative measures could
+form part of the evaluation process for determining new districts, but the
+actual policy will almost surely involve ensembles of measures, both
+quantitative and otherwise, in idealized future redistricting.
 

### 2018-05-04 polygonal-niceness/main.cpp

@@ -9,24 +9,81 @@
 int main()
 {
 
-  auto generator = usa_polygons();
-  auto measurement = chord_arc_infinity;
-  std::string measure = "chord_arc_infinity";
+  // auto generator = usa_polygons();
+  // auto measurement = chord_arc_infinity;
+  // std::string measure = "chord_arc_infinity";
 
-  std::cout << "Running data generation on USA state shape polygons." << std::endl;
+  // std::cout << "Running data generation on USA state shape polygons." << std::endl;
 
-  auto deltas = std::make_tuple(K::FT{1}, K::FT{1}, 1);
+  // auto deltas = std::make_tuple(K::FT{1}, K::FT{1}, 1);
+
+  // std::cout << "Generating data..." << std::endl;
+  // auto data = generate_data(
+  //     generator,
+  //     std::make_tuple(1,2,1),
+  //     deltas,
+  //     measurement);
+  // std::cout << "Success!" << std::endl;
+
+  // std::string output = "data/output/us/";
+  // output += "us_states_" + measure +  ".csv";
+
+  // std::cout << "Writing data to file..." << std::endl;
+  // write_data(
+  //     data,
+  //     deltas,
+  //     output);
+  // std::cout << "Success!" << std::endl;
+
+
+  
+
+
+  int set, start, stop;
+  start = 1;
+  stop = 11;
+  bool smoothed = false;
+  int num_delta = 3;
+
+  std::function<K::FT(Polygon2D)> measurement;
+  std::string measure;
+
+  int version = 2;
+
+  if (version == 1)
+  {
+    measurement = chord_arc_one;
+    measure = "chord_arc_one";
+  }
+  else if (version == 2) 
+  {
+    measurement = chord_arc_infinity;
+    measure = "chord_arc_infinity";
+  } 
+  else 
+  {
+    measurement = alpha_fatness;
+    measure = "alpha_score";
+  }
+
+  std::cout << "Running data generation " << measure << " on Professor Mitchell's polygons." << std::endl;
+  std::cout << "Which data set? ";
+  std::cin >> set;
+  std::cout << std::endl;
+  auto generator = mitchell_polygons(set, start, stop, smoothed);
+
+  auto deltas = std::make_tuple(K::FT{0.05}, K::FT{1.0}, num_delta);
 
   std::cout << "Generating data..." << std::endl;
   auto data = generate_data(
       generator,
-      std::make_tuple(1,2,1),
[…]

### 2018-05-04 paper/main.tex
New abstract
Provisionally done with the paper

@@
 \linenumbers
+
+\setcounter{tocdepth}{1} % -- part,chapters,sections
 
@@
 \begin{abstract}
+  The $\alpha$-fatness and chord-arc scores as measures of the ``niceness'' of
+  polygons are developed and explored, with initial theoretical and empirical
+  results. 
 \end{abstract}
@@
 10, 50, and 100 vertices. In Figure \ref{fig:delta-alpha} and Figure
-\ref{fig:delta-chordarc}, we measure the effect on
+\ref{fig:delta-arc}, we measure the effect on
 polygons of 10 vertices of sweeping $\delta$ between $0.05$ and $1$ on the
@@
 
-\begin{enumerate}
-  \item Comment on the results.
-  \item Talk about applications to Gerrymandering.
-\end{enumerate}
-
-\medskip
-
 \printbibliography[heading=bibintoc]

### 2018-05-04 paper/main.tex
Stray typos

@@
 \newcommand{\abs}[1]{|#1|}
-\newcommand{\chordarc}{{s_{\abs{\partial~\cdot~}}}}
+\newcommand{\chordarc}{{s_{\textrm{arc}}}}
 \DeclareMathOperator{\diam}{\mathrm{diam}}
-\DeclareMathOperator{\conv}{\mathcal{}}
+\DeclareMathOperator{\conv}{\mathcal{CH}}
 
@@
 
-In principal of computing the $\alpha$ and chord-$f$ scores relies on sweeping
+In principal computing the $\alpha$-fatness and chord-$f$ scores relies on sweeping
 the continuum of points of $P$ and evaluating the aforementioned measurements.
@@
     \toprule
-    $\delta$ & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
+    $\delta$ & $P_1$ & $P_2$ & $P_3$ & $P_4$ & $P_5$ & $P_6$ & $P_7$ & $P_8$ & $P_9$ & $P_{10}$ \\
     \midrule
